# Analysis of SPR-EEG data
```{r}
library(ggplot2)
library(eeguana)
library(tidytable)
library(stringr)
library(brms)

setwd("paper")
options(mc.cores = parallel::detectCores())

source("src/util.r")
```

## Comprehension Questions

### Load data
```{r}
responses_df <- list.files(
    "data/spr",
    full.names = TRUE, pattern = "responses_.*\\.csv$"
) |>
    lapply(read_multiple_sessions_csv) |>
    bind_rows() |>
    arrange(participant_number, document_id)

# Familiarity
familiarity_responses <- responses_df |>
    filter(!document_id %in% c(11, 12)) |>
    filter(question_id == 0) |> # zero is familiarity
    select(participant_number, document_id, response) |>
    rename("familiarity_response" = response)

# Content
content_responses <- responses_df |>
    filter(!document_id %in% c(11, 12)) |>
    filter(question_id > 0) |> # zero is familiarity
    group_by(participant_number, document_id) |>
    summarize(
        n_content_correct = sum(correct),
        percent_content_correct = sum(correct) / n()
    )
```

### Plots
Familiarity questions
```{r}
# by story
responses_df |>
    filter(question_id == 0) |> # zero is familiarity
    filter(!document_id %in% c(11, 12)) |>
    ggplot() +
    geom_histogram(aes(x = response, fill = as.numeric(response)), stat = "count") +
    facet_wrap(. ~ story_name, nrow = 2) +
    scale_fill_gradient(low = "lightseagreen", high = "darkseagreen4") +
    theme_light() +
    guides(fill = "none")

# by participant
responses_df |>
    filter(question_id == 0) |> # zero is familiarity
    filter(!document_id %in% c(11, 12)) |>
    ggplot() +
    geom_histogram(aes(x = response, fill = as.numeric(response)), stat = "count") +
    facet_wrap(. ~ participant_number) +
    scale_fill_gradient(low = "lightseagreen", high = "darkseagreen4") +
    theme_light() +
    guides(fill = "none")
```

Content quesions
```{r}
# by story
responses_df |>
    filter(question_id > 0) |> # zero is familiarity
    filter(!document_id %in% c(11, 12)) |>
    mutate(correct = ifelse(correct == 1, "Correct", "Incorrect")) |>
    ggplot() +
    geom_histogram(aes(x = correct, fill = correct), stat = "count") +
    facet_wrap(. ~ story_name) +
    scale_fill_manual(values = c("darkseagreen", "lightseagreen")) +
    theme_light() +
    guides(fill = "none")

# by participant
responses_df |>
    filter(question_id > 0) |> # zero is familiarity
    filter(!document_id %in% c(11, 12)) |>
    mutate(correct = ifelse(correct == 1, "Correct", "Incorrect")) |>
    ggplot() +
    geom_histogram(aes(x = correct, fill = correct), stat = "count") +
    facet_wrap(. ~ participant_number) +
    scale_fill_manual(values = c("darkseagreen", "lightseagreen")) +
    theme_light() +
    guides(fill = "none")
```

## Behavioral data

### Load data
```{r}
stim <- read.csv("data/stim.csv") |>
    mutate(
        lp_quantile = ifelse(
            lp >= quantile(lp, na.rm = TRUE)[4], "high_lp",
            ifelse(lp <= quantile(lp, na.rm = TRUE)[2], "low_lp", "med_lp")
        ),
    )

rt_df <- list.files("data/spr",
    full.names = TRUE,
    pattern = "rt_.*\\.csv$"
) |>
    lapply(read_multiple_sessions_csv) |>
    bind_rows() |>
    mutate( # remove fancy quotations
        word = str_replace_all(word, "\\p{quotation mark}", "'")
    ) |>
    select(-X, -participant_id, -participant_subfix) |>
    left_join(stim,
        by = c("story_name", "document_id", "word_n", "paragraph_n", "word")
    ) |>
    left_join(familiarity_responses,
        by = c("document_id", "participant_number")
    ) |>
    left_join(content_responses, by = c("document_id", "participant_number")) |>
    mutate(
        lp_quantile = ifelse(
            lp >= quantile(lp, na.rm = TRUE)[4], "high_lp",
            ifelse(lp <= quantile(lp, na.rm = TRUE)[2], "low_lp", "med_lp")
        ),
    ) |>
    mutate(rt = reaction_time / 0.001) # reading times in ms instead of s
```

### Models
Log-probability and its spillover
```{r}
data <- rt_df |>
    filter(reading_type == "SPR") |>
    filter(!(document_id %in% c(11, 12)))

m1_rt_formula <- bf(
    rt ~ s_lp + s_lp1 + s_lp2 + s_lp3 +
        (s_lp + s_lp1 + s_lp2 + s_lp3 || participant_number) +
        (s_lp + s_lp1 + s_lp2 + s_lp3 || word)
)

m1_rt_priors <- c(
    prior(normal(5.5, 1), class = Intercept),
    prior(normal(0, .1), class = b),
    prior(normal(.5, .1), class = sigma),
    prior(normal(0, .5), class = sd)
)

m1_rt <- brm(m1_rt_formula,
    family = lognormal(),
    prior = m1_rt_priors,
    data = data,
    chains = 2,
    control = list(adapt_delta = 0.9),
    backend = "cmdstanr",
    file = "src/brms_models/m1_rt"
)

pp_check(m1_rt)
```

```{r}
summary(m1_rt)

mcmc_plot(m1_rt, variable = "^b_[^Intercept]", regex = TRUE)

plot(m1_rt, variable = "^b", regex = TRUE)
```

Log-probability, word length, and their spillover
```{r}
data <- rt_df |>
    filter(reading_type == "SPR") |>
    filter(!(document_id %in% c(11, 12)))

m2_rt_formula <- bf(
    rt ~ s_lp + s_lp1 + s_lp2 + s_lp3 + s_wl + s_wl1 + s_wl2 + s_wl3 +
        (s_lp + s_lp1 + s_lp2 + s_lp3 + s_wl + s_wl1 + s_wl2 + s_wl3 || participant_number) +
        (s_lp + s_lp1 + s_lp2 + s_lp3 + s_wl + s_wl1 + s_wl2 + s_wl3 || word)
)

m2_rt_priors <- c(
    prior(normal(5.5, 1), class = Intercept),
    prior(normal(0, .1), class = b),
    prior(normal(.5, .1), class = sigma),
    prior(normal(0, .5), class = sd)
)

m2_rt <- brm(m2_rt_formula,
    family = lognormal(),
    prior = m2_rt_priors,
    data = data,
    chains = 2,
    control = list(adapt_delta = 0.9),
    backend = "cmdstanr",
    file = "src/brms_models/m2_rt"
)

pp_check(m2_rt)
```

```{r}
summary(m2_rt)

mcmc_plot(m2_rt, variable = "^b_[^Intercept]", regex = TRUE)

plot(m2_rt, variable = "^b_s_lp", regex = TRUE)
plot(m2_rt, variable = "^b_s_wl", regex = TRUE)
```

## EEG

### Load data
```{r}
# read mean_amplitudes
mean_amplitude_df <- read.csv("data/mean_amplitude.csv") |>
    left_join(
        familiarity_responses,
        by = c("document_id", "participant_number")
    ) |>
    left_join(
        content_responses,
        by = c("document_id", "participant_number")
    ) |>
    mutate(
        lp_quantile = factor(lp_quantile,
            levels = c("low_lp", "med_lp", "high_lp")
        )
    )
```


```{r}
# how many epochs was removed due to artifacts?
mean_amplitude_df |>
    filter(!document_id %in% c(11, 12)) |>
    group_by(participant_number) |>
    mutate("n_epochs" = n()) |>
    filter(!is.na(reject_reason)) |>
    group_by(participant_number, reject_reason) |>
    summarize(
        "percent_rejected" = (n() / unique(n_epochs)) * 100
    ) |>
    filter(percent_rejected > 20)

# filter based on amount of rejected epochs
reject_threshold <- 30

reject_df <- mean_amplitude_df |>
    filter(!document_id %in% c(11, 12)) |>
    filter(!is.na(lp_quantile)) |>
    group_by(participant_number, document_id, lp_quantile) |>
    summarize(
        "rejected_epochs" = (sum(is.na(n400)) / n()) * 100
    ) |>
    group_by(participant_number, document_id) |>
    summarize(
        "reject" = ifelse(all(rejected_epochs < reject_threshold), FALSE, TRUE)
    )

mean_amplitude_df <- mean_amplitude_df |>
    left_join(reject_df, by = c("participant_number", "document_id"))
```

```{r}
# read erps
erp_df <- read_filt_erps("data/erps/",
    filename = "data/erp_lp.csv",
    reject_df = reject_df,
    overwrite = FALSE
) |>
    mutate(
        .channel = .key,
        lp_quantile = factor(lp_quantile,
            levels = c("low_lp", "med_lp", "high_lp")
        )
    )
```

### Models
N400 ~ Log-probability in RSVP for nouns, verbs, adjective, and adverbs
```{r}
data <- mean_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "RSVP") |>
    filter(pos %in% c("NOUN", "VERB", "ADJ", "ADV"))

m1_n400_formula <- bf(
    n400 ~ s_lp + (s_lp || participant_number) + (s_lp || word)
)

m1_n400_priors <- c(
    prior(normal(0, 20), class = Intercept),
    prior(normal(0, 10), class = b),
    prior(normal(10, 20), class = sigma),
    prior(normal(0, 10), class = sd)
)

m1_n400 <- brm(m1_n400_formula,
    family = gaussian(),
    prior = m1_n400_priors,
    data = data,
    chains = 2,
    control = list(adapt_delta = 0.9),
    backend = "cmdstanr",
    seed = 246,
    file = "src/brms_models/m1_rsvp_n400"
)

pp_check(m1_n400)
```

```{r}
summary(m1_n400)

mcmc_plot(m1_n400, variable = "^b", regex = TRUE)

plot(m1_n400, variable = "^b", regex = TRUE)
```

N400 ~ Log-probability in SPR for nouns, verbs, adjective, and adverbs
```{r}
data <- mean_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    filter(pos %in% c("NOUN", "VERB", "ADJ", "ADV"))

m2_n400_formula <- bf(
    n400 ~ s_lp + (s_lp || participant_number) + (s_lp || word)
)

m2_n400_priors <- c(
    prior(normal(0, 20), class = Intercept),
    prior(normal(0, 10), class = b),
    prior(normal(10, 20), class = sigma),
    prior(normal(0, 10), class = sd)
)

m2_n400 <- brm(m2_n400_formula,
    family = gaussian(),
    prior = m2_n400_priors,
    data = data,
    chains = 2,
    control = list(adapt_delta = 0.9),
    backend = "cmdstanr",
    seed = 246,
    file = "src/brms_models/m2_spr_n400"
)

pp_check(m2_n400)
```

```{r}
summary(m2_n400)

mcmc_plot(m2_n400, variable = "^b", regex = TRUE)

plot(m2_n400, variable = "^b", regex = TRUE)
```

N170 ~ Log-probability in RSVP for nouns, verbs, adjective, and adverbs
```{r}
data <- mean_amplitude_df |>
    filter(!reject) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "RSVP") |>
    filter(pos %in% c("NOUN", "VERB", "ADJ", "ADV"))

m1_n170_formula <- bf(
    n170 ~ s_lp + (s_lp || participant_number) + (s_lp || word)
)

m1_n170_priors <- c(
    prior(normal(0, 20), class = Intercept),
    prior(normal(0, 10), class = b),
    prior(normal(10, 20), class = sigma),
    prior(normal(0, 10), class = sd)
)

m1_n170 <- brm(m1_n170_formula,
    family = gaussian(),
    prior = m1_n170_priors,
    data = data,
    chains = 2,
    control = list(adapt_delta = 0.9),
    backend = "cmdstanr",
    seed = 246,
    # file = "src/brms_models/m1_rsvp_n170"
)

pp_check(m1_n170)
```

```{r}
summary(m1_n170)

mcmc_plot(m1_n170, variable = "^b", regex = TRUE)

plot(m1_n170, variable = "^b", regex = TRUE)
```

N170 ~ Log-probability in SPR for nouns, verbs, adjective, and adverbs
```{r}
data <- mean_amplitude_df |>
    filter(!reject) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    filter(pos %in% c("NOUN", "VERB", "ADJ", "ADV"))

m2_n170_formula <- bf(
    n170 ~ s_lp + (s_lp || participant_number) + (s_lp || word)
)

m2_n170_priors <- c(
    prior(normal(0, 20), class = Intercept),
    prior(normal(0, 10), class = b),
    prior(normal(10, 20), class = sigma),
    prior(normal(0, 10), class = sd)
)

m2_n170 <- brm(m1_n170_formula,
    family = gaussian(),
    prior = m1_n170_priors,
    data = data,
    chains = 2,
    control = list(adapt_delta = 0.9),
    backend = "cmdstanr",
    seed = 246,
    # file = "src/brms_models/m2_spr_n170"
)

pp_check(m2_n170)
```

```{r}
summary(m2_n170)

mcmc_plot(m2_n170, variable = "^b", regex = TRUE)

plot(m2_n170, variable = "^b", regex = TRUE)
```


### Plots
N400
```{r}
reading_cond <- "RSVP" # SPR or RSVP

erp_df |>
    filter(!.key %in% c("HEOG", "VEOG", "M1", "M2")) |>
    filter(reading_type == reading_cond) |>
    ggplot(aes(x = .time, y = .value)) +
    stat_summary(
        fun = "mean", geom = "line", alpha = 1, linewidth = 1,
        aes(color = lp_quantile)
    ) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    annotate("rect", xmin = .3, xmax = .5, ymin = -Inf, ymax = Inf, alpha = .1, fill = "darkseagreen4") +
    theme_eeguana() +
    theme(legend.position = "bottom")
```

```{r}
reading_cond <- "SPR" # SPR or RSVP

erp_df |>
    filter(.key %in% c(
        "Cz", "Pz", "C4", "CP6", "P4", "P3", "CP5", "C3", "P8", "PO3", "PO4", "P7"
    )) |>
    filter(reading_type == reading_cond) |>
    ggplot(aes(x = .time, y = .value_action_words)) +
    stat_summary(
        fun = "mean", geom = "line", alpha = 1, linewidth = 1,
        aes(color = lp_quantile)
    ) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    annotate("rect", xmin = .3, xmax = .5, ymin = -Inf, ymax = Inf, alpha = .1, fill = "slategray4") +
    eeguana::theme_eeguana() +
    theme(legend.position = "bottom") +
    # facet_wrap(. ~ participant_number) +
    labs(color = "", y = "") +
    scale_color_manual(values = c("steelblue1", "steelblue3", "steelblue4"))

# ggsave(paste("figs/erp_", reading_cond, "_relevant_chs.png", sep = ""), width = 10, height = 10)
```

```{r}
# n400
mean_amplitude_df |>
    filter(!(document_id %in% c(11, 12))) |>
    ggplot(aes(x = lp, y = n400)) +
    geom_point() +
    geom_smooth(method = "lm") +
    theme_light()

mean_amplitude_df |>
    filter(!(document_id %in% c(11, 12))) |>
    ggplot(aes(x = wl, y = n400)) +
    geom_point() +
    geom_smooth(method = "lm") +
    theme_light()

# rt (NB: only in SPR)
mean_amplitude_df |>
    filter(reading_type == "SPR") |>
    filter(!(document_id %in% c(11, 12))) |>
    ggplot(aes(x = lp, y = reaction_time)) +
    geom_point() +
    geom_smooth(method = "lm") +
    theme_light()

mean_amplitude_df |>
    filter(reading_type == "SPR") |>
    filter(!(document_id %in% c(11, 12))) |>
    ggplot(aes(x = wl, y = reaction_time)) +
    geom_point() +
    geom_smooth(method = "lm") +
    theme_light()
```

Early components
```{r}
reading_cond <- "RSVP" # both, SPR, or RSVP

erp_df |>
    filter(.time < .5) |>
    filter(.key %in% c("Pz", "P3", "P7", "O1", "P4", "P8", "O2")) |>
    filter(reading_type == reading_cond) |>
    ggplot(aes(x = .time, y = .value)) +
    stat_summary(
        fun = "mean", geom = "line", alpha = 1, linewidth = 1,
        aes(color = lp_quantile)
    ) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    annotate(
        "rect",
        xmin = .05, xmax = .08, ymin = -Inf, ymax = Inf,
        alpha = .1, fill = "darkseagreen4"
    ) +
    annotate(
        "rect",
        xmin = .08, xmax = .12, ymin = -Inf, ymax = Inf,
        alpha = .1, fill = "darkorange"
    ) +
    annotate(
        "rect",
        xmin = .16, xmax = .2, ymin = -Inf, ymax = Inf,
        alpha = .1, fill = "darkseagreen4"
    ) +
    annotate(
        "rect",
        xmin = .2, xmax = .3, ymin = -Inf, ymax = Inf,
        alpha = .1, fill = "darkorange"
    ) +
    eeguana::theme_eeguana() +
    theme(legend.position = "bottom")
```

Correlation: reading times and n400
```{r}
lp_quantiles <- quantile(mean_amplitude_df$lp, na.rm = TRUE, prob = c(.2, .4, .6, .8, 1))
n <- 0.2
m <- -0.03
mean_amplitude_df |>
    filter(!document_id %in% c(11, 12)) |>
    filter(reading_type == "SPR") |>
    mutate(
        lp_quantile = ifelse(
            lp <= lp_quantiles[1], "0.2", ifelse(
                lp <= lp_quantiles[2], "0.4", ifelse(
                    lp <= lp_quantiles[3], "0.6", ifelse(
                        lp <= lp_quantiles[4], "0.8", ifelse(
                            lp <= lp_quantiles[5], "1", NA
                        )
                    )
                )
            )
        ),
        corrected_n400 = (n400 * m) + n,
        corrected_rt = reaction_time
    ) |>
    filter(!is.na(lp_quantile)) |>
    group_by(lp_quantile) |>
    summarize(
        "mean_N400" = mean(corrected_n400, na.rm = TRUE),
        "sd_N400" = sd(corrected_n400, na.rm = TRUE),
        "mean_ReadingTime" = mean(corrected_rt),
        "sd_ReadingTime" = sd(corrected_rt)
    ) |>
    pivot_longer(
        cols = c(starts_with("mean_"), starts_with("sd_")),
        names_to = c("X", "type"),
        names_pattern = "(.+)_(.+)"
    ) |>
    pivot_wider(names_from = X, values_from = value) |>
    ggplot(aes(x = lp_quantile, y = mean, color = type)) +
    geom_point(size = 5, shape = 15, position = position_dodge(.5)) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = .2, position = position_dodge(.5)
    ) +
    geom_line(aes(group = type), position = position_dodge(.5)) +
    scale_color_manual(values = c("darkseagreen4", "darkorange")) +
    scale_y_continuous(
        name = "Reading Time (ms)", # name first axis
        sec.axis = sec_axis(trans = ~ (. - n) / m, name = "N400 Amplitude (microvolt)")
    ) +
    theme_light() +
    labs(x = "Quantile Log-Probability Words", y = "", color = "")

# ggsave("figs/cor_n400_rt.png", width=10, height=10)
```

```{r}
lp_quantiles <- quantile(mean_amplitude_df$lp, na.rm = TRUE, prob = c(.2, .4, .6, .8, 1))
n <- 0.2
m <- -0.03
mean_amplitude_df |>
    filter(!document_id %in% c(11, 12)) |>
    filter(reading_type == "SPR") |>
    group_by(participant_number, document_id) |>
    mutate(lead_rt = lead(reaction_time)) |>
    mutate(
        lp_quantile = ifelse(
            lp <= lp_quantiles[1], "0.2", ifelse(
                lp <= lp_quantiles[2], "0.4", ifelse(
                    lp <= lp_quantiles[3], "0.6", ifelse(
                        lp <= lp_quantiles[4], "0.8", ifelse(
                            lp <= lp_quantiles[5], "1", NA
                        )
                    )
                )
            )
        ),
        corrected_n400 = (n400 * m) + n,
        corrected_rt = lead_rt
    ) |>
    filter(!is.na(lp_quantile)) |>
    group_by(lp_quantile) |>
    summarize(
        "mean_N400" = mean(corrected_n400, na.rm = TRUE),
        "sd_N400" = sd(corrected_n400, na.rm = TRUE),
        "mean_ReadingTime" = mean(corrected_rt, na.rm = TRUE),
        "sd_ReadingTime" = sd(corrected_rt, na.rm = TRUE)
    ) |>
    pivot_longer(
        cols = c(starts_with("mean_"), starts_with("sd_")),
        names_to = c("X", "type"),
        names_pattern = "(.+)_(.+)"
    ) |>
    pivot_wider(names_from = X, values_from = value) |>
    ggplot(aes(x = lp_quantile, y = mean, color = type)) +
    geom_point(size = 5, shape = 15, position = position_dodge(.5)) +
    geom_errorbar(
        aes(ymin = mean - sd, ymax = mean + sd),
        width = .2, position = position_dodge(.5)
    ) +
    geom_line(aes(group = type), position = position_dodge(.5)) +
    scale_color_manual(values = c("darkseagreen4", "darkorange")) +
    scale_y_continuous(
        name = "Reading Time (ms)", # name first axis
        sec.axis = sec_axis(trans = ~ (. - n) / m, name = "N400 Amplitude (microvolt)")
    ) +
    theme_light() +
    labs(x = "Quantile Log-Probability Words", y = "", color = "")

# ggsave("figs/cor_n400_leadrt.png", width=10, height=10)
```