# Data loss from EEG rejection
Data is removed from EEG data analysis for five reasons:
    1) errors in data collection (3 participants),
    2) manually annotated bad channels or trials,
    3) automatically detected artifacts,
    4) entire texts with number of artifacts reaching threshold of .3,
    5) trials where the reading times was not within thresholds of 100-3,000 ms.

```{r}
library(tidytable)
```

## Summary of participants reaching the artifact reject threshold
```{r}
artifact_threshold <- .3
rt_threshold <- c(100, 3000)

# load EEG components
mean_amplitude_df <- read.csv(file.path("data", "mean_amplitude.csv")) |>
    mutate(
        lp_quantile = factor(lp_quantile,
            levels = c("low_lp", "med_lp", "high_lp")
        ),
        zero_freq = as.logical(zero_freq)
    ) |>
    filter(document_id < 10) |> # filter out practice texts
    group_by(participant_number, document_id) |>
    mutate(
        "rejected_epochs" = (sum(is.na(n400)) / n())
    ) |>
    ungroup()
```

```{r}
# participants for which all texts were removed
completely_removed <- mean_amplitude_df |>
    filter(!participant_number == 64) |> # already excluded
    group_by(participant_number) |>
    mutate("n_docs" = length(unique(document_id))) |>
    filter(rejected_epochs >= artifact_threshold) |>
    filter(length(unique(document_id)) == n_docs) |>
    pull(participant_number) |>
    unique()

completely_removed
```

## EEG data loss for each text (only for the 56 remaning participants)
```{r}
mean_amplitude_df |>
    filter(!participant_number == 64) |> # already excluded
    filter(!participant_number %in% completely_removed) |>
    group_by(participant_number, document_id) |>
    mutate("rejected" = case_when(
        is.na(n400) ~ TRUE,
        rejected_epochs >= artifact_threshold ~ TRUE,
        .default = FALSE
    )) |>
    ungroup() |>
    group_by(document_id) |>
    summarize(
        "percent_rejected" = sum(rejected) / n(),
        "n_participants" = length(unique(participant_number))
    )
```

## Overall data loss from EEG rejection
```{r}
corpus_df <- read.csv(file.path("..", "stimuli", "data", "words_corpus.csv"))

analysis_df <- mean_amplitude_df |>
    # filter word where participant 17 was stopped
    filter(!(participant_number == 17 &
        document_id == 1 &
        number_word == 154)) |>
    filter(participant_number != 64) |> # exclude participant 64
    # reject based on artifact threshold
    group_by(participant_number, document_id) |>
    mutate(
        "rejected_epochs" = (sum(is.na(n400)) / n())
    ) |>
    filter(rejected_epochs < artifact_threshold) |>
    # filter based on reject rt
    mutate(rt = reaction_time / 0.001) |> # reading times in ms instead of s
    filter(rt > rt_threshold[1] & rt < rt_threshold[2]) |>
    ungroup() |>
    filter(!is.na(n400))
```


```{r}
n_words <- corpus_df |>
    filter(document_id < 10) |>
    nrow()
total_trials <- n_words * 71

n_analysis_trials <- analysis_df |> nrow()

n_analysis_trials / total_trials
```

## Number of epochs included (per reading paradigm)
```{r}
analysis_df |>
    group_by(reading_type) |>
    summarise(n())
```