# Early components (<200ms) and word probability
Inspired by the paper by Serena et al. (2020), we're looking at two early components that were found related to contextual predictability.
- 50-80 ms after onset of the word; positive effect of predictability in left- and midline-anterior ROI.
- N1, 160-200 ms after onset of the word; negative effect of predictability in midline- and right-posterior ROI.

```{r}
library(tidytable)
library(eeguana)
library(readxl)
library(stringr)
library(lmerTest)
library(ggplot2)

setwd("paper")

source("src/file_checks.r")
source("src/util.r")
```

## Summarize components
```{r}
### functions (NB: copied from src/summarize_eeg.r)
get_participant_n <- function(file) {
    return(gsub(".*?([0-9]+).*", "\\1", file))
}

cal_mean_amplitude <- function(epochs, chs, time_from, time_to, time_unit) {
    amplitude_mean <- epochs |>
        eeg_filter(between(as_time(.sample, .unit = time_unit), time_from, time_to)) |>
        eeg_group_by(segment, .sample) |>
        eeg_summarize(
            "mean_amplitude_sample" = chs_mean(across(
                chs
            ), na.rm = TRUE)
        ) |>
        eeg_group_by(segment) |>
        eeg_summarize(
            "mean_amplitude" = mean(mean_amplitude_sample)
        )

    return(amplitude_mean)
}
```

```{r}
# Files
epoch_files <- list.files("data/epochs/", full.names = TRUE, pattern = ".rds$")

stim <- read.csv("../data/words_corpus.csv") |>
    select(-X) |>
    mutate(content_word = ifelse(pos %in% c("NOUN", "VERB", "ADJ", "ADV"), TRUE, FALSE)) |>
    mutate(
        lp_quantile = case_when(
            lp >= quantile(lp, na.rm = TRUE)[4] ~ "high_lp",
            lp <= quantile(lp, na.rm = TRUE)[2] ~ "low_lp",
            (lp > quantile(lp, na.rm = TRUE)[2] &
                lp < quantile(lp, na.rm = TRUE)[4]) ~ "med_lp"
        ),
        lp_quantile_content = case_when(
            content_word == TRUE ~ case_when(
                (lp >= quantile(lp[content_word == TRUE], na.rm = TRUE)[4]
                ~ "high_lp"),
                (lp <= quantile(lp[content_word == TRUE], na.rm = TRUE)[2]
                ~ "low_lp"),
                (lp > quantile(lp[content_word == TRUE], na.rm = TRUE)[2] &
                    lp < quantile(lp[content_word == TRUE], na.rm = TRUE)[4])
                ~ "med_lp"
            ),
            TRUE ~ NA_character_
        )
    )

exclude_df <- read_excel("data/exclude.xlsx")

chs <- list(
    "midline-anterior" = c("AFz", "Fz"),
    "left-anterior" = c("Fp1", "AF3", "F7", "F5", "F3", "F1"),
    "midline-posterior" = c("Pz", "POz"),
    "right-posterior" = c("P2", "P4", "P6", "P8", "PO4", "PO8", "O2")
)
```

```{r}
filename <- "data/early_components.csv"

# already summarized data
if (file.exists(filename)) {
    cur_mean_df <- read.csv(filename)
    cur_mean_participants <- unique(cur_mean_df$participant_number)
} else {
    cur_mean_participants <- c()
}

## loop through files
for (epoch_file in epoch_files) {
    start_time <- Sys.time()
    char_n <- get_participant_n(epoch_file)
    n <- as.numeric(char_n)
    if (n %in% cur_mean_participants) {
        print(paste("Participant", n, "already in", filename))
        next
    }
    print(
        paste("Running participant: ", n, sep = "")
    )

    # load data
    exclude_chs <- exclude_df |>
        filter(participant_number == n & !is.na(ch)) |>
        pull(ch)
    epochs <- readRDS(epoch_file) |>
        as_eeg_lst() |>
        eeg_left_join(stim)
    rt_df <- list.files(
        "data/spr",
        full.names = TRUE,
        pattern = paste("rt_.*_", n, "_.*\\.csv$", sep = "")
    ) |>
        lapply(read_multiple_sessions_csv) |>
        bind_rows() |>
        mutate( # remove fancy quotations
            word = str_replace_all(word, "\\p{quotation mark}", "'"),
            trial = ifelse(document_id > 10, trial - 0.5, trial)
        ) |>
        select(-X, -participant_id, -participant_subfix) |>
        left_join(
            stim,
            by = c("story_name", "document_id", "word_n", "paragraph_n", "word")
        ) |>
        arrange(trial, paragraph_n, word_n)
    rt_df$segment <- seq_len(nrow(rt_df))
    reject_reasons <- epochs |>
        segments_tbl() |>
        select(reject_reason, segment)
    rt_df <- rt_df |> left_join(reject_reasons)

    # summarize results
    early_chs <- c(chs[["midline-anterior"]], chs[["left-anterior"]])
    early_chs <- early_chs[!early_chs %in% exclude_chs] # exclude
    amplitude_early <- cal_mean_amplitude(
        epochs,
        chs = early_chs,
        time_from = .05,
        time_to = .08,
        time_unit = "s"
    )

    n1_chs <- c(chs[["midline-posterior"]], chs[["right-posterior"]])
    n1_chs <- n1_chs[!n1_chs %in% exclude_chs] # exclude
    amplitude_n1 <- cal_mean_amplitude(
        epochs,
        chs = n1_chs,
        time_from = .16,
        time_to = .2,
        time_unit = "s"
    )

    tmp_df <- amplitude_early |>
        as_tidytable() |>
        rename("early_component" = .value) |>
        select(-.key) |>
        left_join(
            amplitude_n1 |>
                as_tidytable() |>
                rename("n1" = .value) |>
                select(-.key)
        ) |>
        left_join(rt_df, by = "segment")

    # if (exists("early_amplitude_df")) {
    #     early_amplitude_df <- rbind(early_amplitude_df, tmp_df)
    # } else {
    #     early_amplitude_df <- tmp_df
    # }

    end_time <- Sys.time()
    print(paste("Time for participant", n, ":", end_time - start_time))

    write.table(
        tmp_df,
        filename,
        sep = ",",
        col.names = !file.exists(filename),
        row.names = FALSE,
        append = TRUE
    )
}
```

## Test models with lmer
```{r}
early_amplitude_df <- read.csv("data/early_components.csv")
```

```{r}
# check number of words per participant is correct
test_n_words_per_participants(early_amplitude_df)
```

```{r}
# filter based on amount of rejected epochs
reject_threshold <- .3

reject_df <- early_amplitude_df |>
    filter(!document_id %in% c(11, 12)) |>
    filter(!is.na(lp_quantile)) |>
    group_by(participant_number, document_id, lp_quantile) |>
    summarize(
        "rejected_epochs" = (sum(is.na(n1)) / n())
    ) |>
    group_by(participant_number, document_id) |>
    summarize(
        "reject" = ifelse(all(rejected_epochs < reject_threshold), FALSE, TRUE)
    )

reject_df |>
    filter(reject) |>
    group_by(participant_number) |>
    summarize(n())

early_amplitude_df <- early_amplitude_df |>
    left_join(reject_df, by = c("participant_number", "document_id"))
```

```{r}
data <- early_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    # filter based on reject rt
    mutate(rt = reaction_time / 0.001) |> # reading times in ms instead of s
    filter(rt > 100 & rt < 3000) |>
    filter(!participant_number == 64)

early_m <- lmer(
    (early_component ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = data
)

early_m1 <- lmer(
    (early_component ~ s_lp + s_freq +
        (s_lp + s_freq | participant_number) +
        (s_lp | word) +
        (s_lp + s_freq | document_id)
    ),
    data = data
)

n1_m <- lmer(
    (n1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = data
)

n1_m1 <- lmer(
    (n1 ~ s_lp + s_freq +
        (s_lp + s_freq | participant_number) +
        (s_lp | word) +
        (s_lp + s_freq | document_id)
    ),
    data = data
)

n1_m2 <- lmer(
    (n1 ~ s_lp * s_freq +
        (s_lp * s_freq | participant_number) +
        (s_lp | word) +
        (s_lp * s_freq | document_id)
    ),
    data = data
)

n1_m3 <- lmer(
    (n1 ~ s_freq +
        (s_freq | participant_number) +
        (s_freq | document_id)
    ),
    data = data
)
```

```{r}
summary(early_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (early_component ~ s_lp + (s_lp | participant_number) + (s_lp |
    word) + (s_lp | document_id))
   Data: data

REML criterion at convergence: 829696

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-8.9251 -0.6266 -0.0029  0.6315 10.2835

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept)  0.101111 0.31798
                    s_lp         0.059875 0.24469  -0.47
 participant_number (Intercept)  2.368495 1.53899       
                    s_lp         0.001051 0.03241  1.00
 document_id        (Intercept)  0.007160 0.08461
                    s_lp         0.002509 0.05009  0.42
 Residual                       97.785442 9.88865       
Number of obs: 111761, groups:
word, 1975; participant_number, 51; document_id, 8

Fixed effects:
             Estimate Std. Error        df t value Pr(>|t|)  
(Intercept)  0.414103   0.221529 52.247792   1.869   0.0672 .
s_lp         0.003917   0.040972  9.109582   0.096   0.9259
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp 0.148
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(early_m1)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula:
(early_component ~ s_lp + s_freq + (s_lp + s_freq | participant_number) +
    (s_lp | word) + (s_lp + s_freq | document_id))
   Data: data

REML criterion at convergence: 829695.8

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-8.9180 -0.6268 -0.0030  0.6318 10.2716

Random effects:
 Groups             Name        Variance  Std.Dev. Corr       
 word               (Intercept) 9.669e-02 0.31095
                    s_lp        6.042e-02 0.24580  -0.46
 participant_number (Intercept) 2.369e+00 1.53924
                    s_lp        1.139e-04 0.01067  -0.57
                    s_freq      5.834e-03 0.07638   0.88 -0.89
 document_id        (Intercept) 6.972e-03 0.08350
                    s_lp        6.531e-03 0.08082   0.27
                    s_freq      1.554e-03 0.03942  -0.22 -1.00
 Residual                       9.778e+01 9.88854
Number of obs: 111761, groups:
word, 1975; participant_number, 51; document_id, 8

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)
(Intercept)  0.42084    0.22158 52.25223   1.899   0.0631 .
s_lp        -0.01074    0.05037  6.82543  -0.213   0.8374
s_freq       0.03036    0.04420 15.42366   0.687   0.5023
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr) s_lp  
s_lp    0.005
s_freq  0.226 -0.534
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(n1_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |
    document_id))
   Data: data

REML criterion at convergence: 835325.8

Scaled residuals:
     Min       1Q   Median       3Q      Max 
-13.0567  -0.6111  -0.0011   0.6097  10.0569

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 7.063e-01  0.84044
                    s_lp        1.458e-02  0.12074 0.42
 participant_number (Intercept) 3.178e+00  1.78275
                    s_lp        9.848e-02  0.31382 -0.40
 document_id        (Intercept) 1.469e-03  0.03833
                    s_lp        1.770e-02  0.13304 -0.60
 Residual                       1.025e+02 10.12393
Number of obs: 111761, groups:
word, 1975; participant_number, 51; document_id, 8

Fixed effects:
              Estimate Std. Error         df t value Pr(>|t|)
(Intercept) -0.3813964  0.2551479 50.1632957  -1.495    0.141
s_lp        -0.0005294  0.0779580 18.3348288  -0.007    0.995

Correlation of Fixed Effects:
     (Intr)
s_lp -0.214
optimizer (nloptwrap) convergence code: 0 (OK)
Model failed to converge with max|grad| = 0.0308431 (tol = 0.002, component 1)

```{r}
summary(n1_m1)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp + s_freq + (s_lp + s_freq | participant_number) +
    (s_lp | word) + (s_lp + s_freq | document_id))
   Data: data

REML criterion at convergence: 835267

Scaled residuals:
     Min       1Q   Median       3Q      Max 
-13.0911  -0.6115  -0.0009   0.6088  10.0846

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 5.538e-01  0.74420
                    s_lp        1.105e-02  0.10512 0.06
 participant_number (Intercept) 3.170e+00  1.78052
                    s_lp        7.315e-02  0.27046 -0.44      
                    s_freq      8.136e-02  0.28524 -0.03 -0.02
 document_id        (Intercept) 1.078e-03  0.03283
                    s_lp        2.345e-02  0.15315  0.08
                    s_freq      3.506e-03  0.05921 -0.29 -0.98
 Residual                       1.025e+02 10.12291
Number of obs: 111761, groups:
word, 1975; participant_number, 51; document_id, 8

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)    
(Intercept) -0.50547    0.25502 50.16948  -1.982    0.053 .
s_lp         0.08418    0.08070 12.51070   1.043    0.317
s_freq      -0.31643    0.07038 37.67362  -4.496 6.41e-05 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr) s_lp
s_lp   -0.193
s_freq  0.031 -0.367
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(n1_m2)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp * s_freq + (s_lp * s_freq | participant_number) +
    (s_lp | word) + (s_lp * s_freq | document_id))
   Data: data

REML criterion at convergence: 835266

Scaled residuals:
     Min       1Q   Median       3Q      Max 
-13.0918  -0.6114  -0.0014   0.6088  10.0468

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept)   0.54667  0.73937
                    s_lp          0.01059  0.10291 0.08
 participant_number (Intercept)   3.17903  1.78298
                    s_lp          0.09641  0.31050 -0.44
                    s_freq        0.07581  0.27534 -0.03  0.05
                    s_lp:s_freq   0.00450  0.06708 -0.25  0.77  0.62
 document_id        (Intercept)   0.01541  0.12412
                    s_lp          0.05265  0.22947 -0.65
                    s_freq        0.01617  0.12716  0.81 -0.93      
                    s_lp:s_freq   0.01382  0.11756 -0.95  0.79 -0.94
 Residual                       102.46620 10.12256
Number of obs: 111761, groups:
word, 1975; participant_number, 51; document_id, 8

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)   
(Intercept) -0.49010    0.25926 51.06155  -1.890   0.0644 .
s_lp         0.06052    0.11198  9.93523   0.540   0.6008
s_freq      -0.30654    0.08059 13.74662  -3.804   0.0020 **
s_lp:s_freq -0.02742    0.06340  7.60423  -0.433   0.6774   
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
            (Intr) s_lp   s_freq
s_lp        -0.258
s_freq       0.109 -0.482
s_lp:s_freq -0.175  0.711 -0.309
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(n1_m3)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_freq + (s_freq | participant_number) + (s_freq | document_id))
   Data: data

REML criterion at convergence: 836593.3

Scaled residuals:
     Min       1Q   Median       3Q      Max 
-13.1271  -0.6144  -0.0010   0.6111  10.0953

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 participant_number (Intercept) 3.150e+00  1.77469
                    s_freq      9.801e-02  0.31307 -0.23
 document_id        (Intercept) 8.851e-03  0.09408
                    s_freq      4.914e-03  0.07010 -1.00
 Residual                       1.030e+02 10.15017
Number of obs: 111915, groups:  participant_number, 51; document_id, 8

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)    
(Intercept) -0.59487    0.25368 49.55151  -2.345   0.0231 *
s_freq      -0.40025    0.06101 24.39389  -6.560 8.07e-07 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr)
s_freq -0.220
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

## Plots
```{r}
early_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    # filter based on reject rt
    mutate(rt = reaction_time / 0.001) |> # reading times in ms instead of s
    filter(rt > 100 & rt < 3000) |>
    filter(!participant_number == 64) |>
    ggplot(aes(x = s_lp, y = early_component)) +
    geom_point(aes(color = participant_number), alpha = .1) +
    geom_smooth(method = "lm") +
    theme_minimal()
```

```{r}
early_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    # filter based on reject rt
    mutate(rt = reaction_time / 0.001) |> # reading times in ms instead of s
    filter(rt > 100 & rt < 3000) |>
    filter(!participant_number == 64) |>
    ggplot(aes(x = s_lp, y = n1)) +
    geom_point(aes(color = participant_number), alpha = .1) +
    geom_smooth(method = "lm") +
    theme_minimal()
```

```{r}
early_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    # filter based on reject rt
    mutate(rt = reaction_time / 0.001) |> # reading times in ms instead of s
    filter(rt > 100 & rt < 3000) |>
    filter(!participant_number == 64) |>
    ggplot(aes(x = s_freq, y = n1)) +
    geom_point(aes(color = participant_number), alpha = .1) +
    geom_smooth(method = "lm") +
    theme_minimal()
```

```{r}
early_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    # filter based on reject rt
    mutate(rt = reaction_time / 0.001) |> # reading times in ms instead of s
    filter(rt > 100 & rt < 3000) |>
    filter(!participant_number == 64) |>
    mutate(
        freq_quantile = case_when(
            zipf_freq >= quantile(zipf_freq, na.rm = TRUE)[4] ~ "high_freq",
            zipf_freq <= quantile(zipf_freq, na.rm = TRUE)[2] ~ "low_freq",
            (zipf_freq > quantile(zipf_freq, na.rm = TRUE)[2] &
                zipf_freq < quantile(zipf_freq, na.rm = TRUE)[4]) ~ "med_freq"
        )
    ) |>
    ggplot(aes(x = s_lp, y = n1)) +
    geom_point(aes(color = participant_number), alpha = .1) +
    geom_smooth(method = "lm") +
    facet_wrap(. ~ freq_quantile) +
    theme_minimal()
```

## with brms
```{r}
library(brms)

options(mc.cores = parallel::detectCores())
options(brms.backend = "cmdstan")
```

```{r}

```