# Early components (<200ms) and word probability
Inspired by the paper by Serena et al. (2020), we're looking at two early components that were found related to contextual predictability.
- 50-80 ms after onset of the word; positive effect of predictability in left- and midline-anterior ROI.
- N1, 160-200 ms after onset of the word; negative effect of predictability in midline- and right-posterior ROI.

```{r}
library(tidytable)
library(eeguana)
library(readxl)
library(stringr)
library(lmerTest)
library(ggplot2)

setwd("paper")

source("src/util.r")
```

## Summarize components
```{r}
### functions (NB: copied from src/summarize_eeg.r)
get_participant_n <- function(file) {
    return(gsub(".*?([0-9]+).*", "\\1", file))
}

cal_mean_amplitude <- function(epochs, chs, time_from, time_to, time_unit) {
    amplitude_mean <- epochs |>
        eeg_filter(between(as_time(.sample, .unit = time_unit), time_from, time_to)) |>
        eeg_group_by(segment, .sample) |>
        eeg_summarize(
            "mean_amplitude_sample" = chs_mean(across(
                chs
            ), na.rm = TRUE)
        ) |>
        eeg_group_by(segment) |>
        eeg_summarize(
            "mean_amplitude" = mean(mean_amplitude_sample)
        )

    return(amplitude_mean)
}
```

```{r}
# Files
epoch_files <- list.files("data/epochs/", full.names = TRUE, pattern = ".rds$")

stim <- read.csv("../data/words_corpus.csv") |>
    select(-X) |>
    mutate(content_word = ifelse(pos %in% c("NOUN", "VERB", "ADJ", "ADV"), TRUE, FALSE)) |>
    mutate(
        lp_quantile = case_when(
            lp >= quantile(lp, na.rm = TRUE)[4] ~ "high_lp",
            lp <= quantile(lp, na.rm = TRUE)[2] ~ "low_lp",
            (lp > quantile(lp, na.rm = TRUE)[2] &
                lp < quantile(lp, na.rm = TRUE)[4]) ~ "med_lp"
        ),
        lp_quantile_content = case_when(
            content_word == TRUE ~ case_when(
                (lp >= quantile(lp[content_word == TRUE], na.rm = TRUE)[4]
                ~ "high_lp"),
                (lp <= quantile(lp[content_word == TRUE], na.rm = TRUE)[2]
                ~ "low_lp"),
                (lp > quantile(lp[content_word == TRUE], na.rm = TRUE)[2] &
                    lp < quantile(lp[content_word == TRUE], na.rm = TRUE)[4])
                ~ "med_lp"
            ),
            TRUE ~ NA_character_
        )
    )

exclude_df <- read_excel("data/exclude.xlsx")

chs <- list(
    "midline-anterior" = c("AFz", "Fz"),
    "left-anterior" = c("Fp1", "AF3", "F7", "F5", "F3", "F1"),
    "midline-posterior" = c("Pz", "POz"),
    "right-posterior" = c("P2", "P4", "P6", "P8", "PO4", "PO8", "O2")
)
```

```{r}
filename <- "data/early_components.csv"

# already summarized data
if (file.exists(filename)) {
    cur_mean_df <- read.csv(filename)
    cur_mean_participants <- unique(cur_mean_df$participant_number)
} else {
    cur_mean_participants <- c()
}

## loop through files
for (epoch_file in epoch_files) {
    start_time <- Sys.time()
    char_n <- get_participant_n(epoch_file)
    n <- as.numeric(char_n)
    if (n %in% cur_mean_participants) {
        print(paste("Participant", n, "already in", filename))
        next
    }
    print(
        paste("Running participant: ", n, sep = "")
    )

    # load data
    exclude_chs <- exclude_df |>
        filter(participant_number == n & !is.na(ch)) |>
        pull(ch)
    epochs <- readRDS(epoch_file) |>
        as_eeg_lst() |>
        eeg_left_join(stim)
    rt_df <- list.files(
        "data/spr",
        full.names = TRUE,
        pattern = paste("rt_.*_", n, "_.*\\.csv$", sep = "")
    ) |>
        lapply(read_multiple_sessions_csv) |>
        bind_rows() |>
        mutate( # remove fancy quotations
            word = str_replace_all(word, "\\p{quotation mark}", "'"),
            trial = ifelse(document_id > 10, trial - 0.5, trial)
        ) |>
        select(-X, -participant_id, -participant_subfix) |>
        left_join(
            stim,
            by = c("story_name", "document_id", "word_n", "paragraph_n", "word")
        ) |>
        arrange(trial, paragraph_n, word_n)
    rt_df$segment <- seq_len(nrow(rt_df))
    reject_reasons <- epochs |>
        segments_tbl() |>
        select(reject_reason, segment)
    rt_df <- rt_df |> left_join(reject_reasons)

    # summarize results
    early_chs <- c(chs[["midline-anterior"]], chs[["left-anterior"]])
    early_chs <- early_chs[!early_chs %in% exclude_chs] # exclude
    amplitude_early <- cal_mean_amplitude(
        epochs,
        chs = early_chs,
        time_from = .05,
        time_to = .08,
        time_unit = "s"
    )

    n1_chs <- c(chs[["midline-posterior"]], chs[["right-posterior"]])
    n1_chs <- n1_chs[!n1_chs %in% exclude_chs] # exclude
    amplitude_n1 <- cal_mean_amplitude(
        epochs,
        chs = n1_chs,
        time_from = .16,
        time_to = .2,
        time_unit = "s"
    )

    tmp_df <- amplitude_early |>
        as_tidytable() |>
        rename("early_component" = .value) |>
        select(-.key) |>
        left_join(
            amplitude_n1 |>
                as_tidytable() |>
                rename("n1" = .value) |>
                select(-.key)
        ) |>
        left_join(rt_df, by = "segment")

    # if (exists("early_amplitude_df")) {
    #     early_amplitude_df <- rbind(early_amplitude_df, tmp_df)
    # } else {
    #     early_amplitude_df <- tmp_df
    # }

    end_time <- Sys.time()
    print(paste("Time for participant", n, ":", end_time - start_time))

    write.table(
        tmp_df,
        filename,
        sep = ",",
        col.names = !file.exists(filename),
        row.names = FALSE,
        append = TRUE
    )
}
```

## Test models with lmer
```{r}
early_amplitude_df <- read.csv("data/early_components.csv")
```

```{r}
# check data
early_amplitude_df |>
    group_by(participant_number) |>
    summarise(n()) |>
    print(n = 21)
```

```{r}
# filter based on amount of rejected epochs
reject_threshold <- .3

reject_df <- early_amplitude_df |>
    filter(!document_id %in% c(11, 12)) |>
    filter(!is.na(lp_quantile)) |>
    group_by(participant_number, document_id, lp_quantile) |>
    summarize(
        "rejected_epochs" = (sum(is.na(n1)) / n())
    ) |>
    group_by(participant_number, document_id) |>
    summarize(
        "reject" = ifelse(all(rejected_epochs < reject_threshold), FALSE, TRUE)
    )

reject_df |>
    filter(reject) |>
    group_by(participant_number) |>
    summarize(n())

early_amplitude_df <- early_amplitude_df |>
    left_join(reject_df, by = c("participant_number", "document_id"))
```

```{r}
data <- early_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR")

early_m <- lmer(
    (early_component ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = data
)

n1_m <- lmer(
    (n1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = data
)
```

```{r}
summary(early_m)
```

```{r}
summary(n1_m)
```

## Plots
```{r}
early_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    ggplot(aes(x = s_lp, y = early_component)) +
    geom_point(aes(color = participant_number), alpha = .1) +
    geom_smooth(method = "lm") +
    theme_minimal()
```

```{r}
early_amplitude_df |>
    filter(!(reject)) |>
    filter(!(document_id %in% c(11, 12))) |>
    filter(reading_type == "SPR") |>
    ggplot(aes(x = s_lp, y = n1)) +
    geom_point(aes(color = participant_number), alpha = .1) +
    geom_smooth(method = "lm") +
    theme_minimal()
```