# Plot of ERPS
```{r}
library(ggplot2)
library(eeguana)
library(tidytable)
library(akima)
library(tibble)
library(patchwork)

setwd("paper")

figs_path <- file.path("figs", "erps")
dir.create(figs_path)
```

## load data
```{r}
erp_df <- read.csv("data/erp_lp.csv") |>
    mutate(
        lp_quantile = factor(lp_quantile,
            levels = c("low_lp", "med_lp", "high_lp")
        )
    )
```

```{r}
n400_chs <- c(
    "Cz", "Pz", "C4", "CP6", "P4", "P3",
    "CP5", "C3", "P8", "PO3", "PO4", "P7"
)
p600_chs <- c(
    "Cz", "CP2", "Pz", "CP1", "C4", "CP6",
    "P4", "P3", "CP5", "C3", "T8", "TP8",
    "P8", "PO3", "PO4", "P7", "TP7", "T7"
)

n400_timewindow <- c(.3, .5)
p600_timewindow <- c(.5, .7)
```

## plotting functions
```{r}
erp_mean_plot <- function(
    df,
    reading_cond,
    channels = c("all"),
    content_words = FALSE,
    annotate_timewindow = FALSE) {
    # filter channels
    if (channels[1] == "all" && length(channels) == 1) {
        df <- df |>
            filter(!.key %in% c("HEOG", "VEOG", "M1", "M2"))
    } else {
        df <- df |>
            filter(.key %in% channels)
    }

    # specify value col
    if (content_words) {
        df <- df |>
            mutate("value" = .value_content_words)
    } else {
        df <- df |>
            mutate("value" = .value)
    }

    p <- df |>
        filter(reading_type == reading_cond) |>
        mutate(
            "lp_quantile" = case_when(
                lp_quantile == "low_lp" ~ "<25%",
                lp_quantile == "med_lp" ~ "25%-75%",
                lp_quantile == "high_lp" ~ ">75%",
            )
        ) |>
        mutate(
            lp_quantile = factor(lp_quantile,
                levels = c("<25%", "25%-75%", ">75%")
            )
        ) |>
        ggplot(aes(x = .time, y = value)) +
        stat_summary(
            fun = "mean", geom = "line", alpha = 1, linewidth = 1,
            aes(color = lp_quantile)
        ) +
        geom_vline(xintercept = 0, linetype = "dashed") +
        eeguana::theme_eeguana() +
        # theme(legend.position = "bottom") +
        labs(y = "\u03BCV", x = "time (ms)", color = "Quantile \nLog-probability") +
        scale_color_manual(values = c("steelblue1", "steelblue3", "steelblue4"))

    if (!isFALSE(annotate_timewindow)) {
        p <- p + annotate("rect",
            xmin = annotate_timewindow[1], xmax = annotate_timewindow[2],
            ymin = -Inf, ymax = Inf,
            alpha = .1, fill = "slategray4"
        )
    }

    return(p)
}
```

```{r}
erp_facet_plot <- function(
    df,
    reading_cond,
    channels = c("all"),
    content_words = FALSE,
    annotate_timewindow = FALSE) {
    # filter channels
    if (channels[1] == "all" && length(channels) == 1) {
        df <- df |>
            filter(!.key %in% c("HEOG", "VEOG", "M1", "M2"))
    } else {
        df <- df |>
            filter(.key %in% channels)
    }

    # specify value col
    if (content_words) {
        df <- df |>
            mutate("value" = .value_content_words)
    } else {
        df <- df |>
            mutate("value" = .value)
    }

    p <- df |>
        filter(reading_type == reading_cond) |>
        mutate(
            "lp_quantile" = case_when(
                lp_quantile == "low_lp" ~ "<25%",
                lp_quantile == "med_lp" ~ "25%-75%",
                lp_quantile == "high_lp" ~ ">75%",
            )
        ) |>
        mutate(
            lp_quantile = factor(lp_quantile,
                levels = c("<25%", "25%-75%", ">75%")
            )
        ) |>
        ggplot(aes(x = .time, y = value)) +
        geom_line(aes(color = lp_quantile), linewidth = 1) +
        geom_vline(xintercept = 0, linetype = "dashed") +
        eeguana::theme_eeguana() +
        facet_wrap(. ~ .key) +
        theme(legend.position = "bottom") +
        labs(y = "\u03BCV", x = "time (ms)", color = "Quantile Log-probability") +
        scale_color_manual(values = c("steelblue1", "steelblue3", "steelblue4"))

    if (!isFALSE(annotate_timewindow)) {
        p <- p + annotate("rect",
            xmin = annotate_timewindow[1], xmax = annotate_timewindow[2],
            ymin = -Inf, ymax = Inf,
            alpha = .1, fill = "slategray4"
        )
    }

    return(p)
}
```

## Plots
ERP averaged over all channels for all words
```{r}
reading_cond <- "SPR"

erp_mean_plot(
    df = erp_df,
    reading_cond = reading_cond
)
```

ERPs averaged over channels used for calculating mean amplitudes of components (n400 and p600)
```{r}
reading_cond <- "SPR"
erp_component <- "p600"
only_content_words <- TRUE

if (erp_component == "n400") {
    chs <- n400_chs
    timewindow <- n400_timewindow
} else if (erp_component == "p600") {
    chs <- p600_chs
    timewindow <- p600_timewindow
}

erp_mean_plot(
    df = erp_df,
    reading_cond = reading_cond,
    channels = chs,
    content_words = only_content_words,
    annotate_timewindow = timewindow
) + theme(legend.position = "bottom")

ggsave(
    file.path(
        figs_path,
        paste(reading_cond, "_", erp_component, "_contentwords",
            only_content_words, ".pdf",
            sep = ""
        )
    ),
    width = 4, height = 2.5
)
```

ERPs in channels seperately
```{r}
reading_cond <- "SPR"
erp_component <- "n400"
only_content_words <- TRUE

if (erp_component == "n400") {
    chs <- n400_chs
    timewindow <- n400_timewindow
} else if (erp_component == "p600") {
    chs <- p600_chs
    timewindow <- p600_timewindow
}

erp_facet_plot(
    df = filt_df,
    reading_cond = reading_cond,
    # channels = chs,
    content_words = only_content_words,
    # annotate_timewindow = timewindow
) |> plot_in_layout()

ggsave(
    file.path(
        figs_path, "plot_in_layout_32.png"
        # paste(reading_cond, "_", erp_component, "_contentwords",
        #     only_content_words, "_facet_chs.png",
        #     sep = ""
        # )
    ),
    width = 10, height = 12
)
```

## Plot in layout
Function from eeguana (https://github.com/bnicenboim/eeguana/blob/master/R/plot_helpers.R and https://github.com/bnicenboim/eeguana/blob/master/R/plot.R)
```{r}
#' Looks for grobs matching a pattern. Almost identical to gtable::gtable_filter
#'
#' Looks for grobs matching a pattern. Almost identical to gtable::gtable_filter
#' @param x gtable
#' @param pattern regex
#' @noRd
g_filter <-
    function(x, pattern, trim = TRUE) {
        matches <- grepl(pattern, x$layout$name)
        x$layout <- x$layout[matches, , drop = FALSE]
        x$grobs <- x$grobs[matches]
        if (trim) {
            gtable_trim(x)
        } else {
            x
        }
    }
#' Looks for grobs not matching a pattern. Opposite of gtable::gtable_filter
#'
#' Looks for grobs not matching a pattern. Opposite of gtable::gtable_filter
#' @param x gtable
#' @param pattern regex
#' @noRd
g_filter_out <- function(x, pattern, trim) {
    matches <- grepl(pattern, x$layout$name)
    x$layout <- x$layout[!matches, , drop = FALSE]
    x$grobs <- x$grobs[!matches]
    if (trim) {
        gtable_trim(x)
    } else {
        x
    }
}

plot_in_layout.gg <- function(plot, .projection = "polar", .ratio = c(1, 1)) {
    size_x <- .ratio[[1]]
    size_y <- .ratio[[2]]
    ch_location <- layout_32_1020 |> rename(".key" = .channel)
    ## if (!"channel" %in% colnames(ch_location)) {
    ##   stop("Channels are missing from the data.")
    ## }
    if (!all(c(".x", ".y", ".z") %in% colnames(ch_location))) {
        stop("Coordinates are missing from the data.")
    }
    plot <- plot + ggplot2::facet_wrap(. ~ .key)
    plot_grob <- ggplot2::ggplotGrob(plot)
    layout <- ggplot2::ggplot_build(plot)$layout$layout

    ## PANEL ROW COL channel SCALE_X SCALE_Y
    ## 1      1   1   1     Fp1       1       1
    ## 2      2   1   2     Fpz       1       1
    ## 3      3   1   3     Fp2       1       1
    ## 4      4   1   4      F7       1       1
    ## 5      5   1   5      F3       1       1
    ## 6      6   1   6      Fz       1       1
    ## 7      7   2   1      F4       1       1

    # The facet in the bottom left has both axis, I'll extract and use everywhere:
    maxrow <- max(layout$ROW) # bottom
    # first I extract the axis and I fill the grob with it.
    axisl <- g_filter(plot_grob, paste0("axis-l-", maxrow, "-1"))
    axisb <- g_filter(plot_grob, paste0("axis-b-1-", maxrow))

    # # then I also extract the labels, which I'll use for each facet
    axes_labels <- g_filter(plot_grob, ".lab-.")

    # This the complete facet with axis
    panel_txt <- paste0("panel-", maxrow, "-1")
    strip_txt <- paste0("strip-t-1-", maxrow)
    axisl_txt <- paste0("axis-l-", maxrow, "-1")
    axisb_txt <- paste0("axis-b-1-", maxrow)
    pattern_txt <- paste0(c(panel_txt, strip_txt, axisl_txt, axisb_txt), collapse = "|")
    full_facet_grob <- g_filter(plot_grob, pattern_txt, trim = TRUE)

    rowsize <- full_facet_grob$heights[3] # bottom
    colsize <- full_facet_grob$widths[1] # left

    # needed for passing checks:
    b <- NULL
    l <- NULL
    # THESE ARE NOT IN ORDER!!!
    panels <- subset(plot_grob$layout, grepl("panel", plot_grob$layout$name)) %>%
        dplyr::arrange(b, l)
    strips <- subset(plot_grob$layout, grepl("strip", plot_grob$layout$name)) %>%
        dplyr::arrange(b, l)

    # won't work for free scales, need to add an if-else inside

    channel_grobs <- purrr::map(layout$.key, function(ch) {
        ## pos <- which(facet_names==ch, arr.ind =  TRUE)
        ch_pos <- layout %>% dplyr::filter(.key == ch)
        # panel_txt <- paste0("panel-", ch_pos$ROW, "-", ch_pos$COL)
        # strip_txt <- paste0("strip-t-", ch_pos$COL, "-", ch_pos$ROW)
        # axisl_txt <- paste0("axis-l-", ch_pos$ROW, "-", ch_pos$COL)
        # axisb_txt <- paste0("axis-b-", ch_pos$COL, "-", ch_pos$ROW)
        # # pattern_txt <- paste0(c(panel_txt,strip_txt,axisl_txt,axisb_txt), collapse = "|")
        # pattern_txt <- paste0(c(panel_txt, strip_txt), collapse = "|")
        # # plot_grob[[1]][[which(plot_grob$layout$name == axisl_txt)]] <- axisl[[1]][[1]]
        # # plot_grob[[1]][[which(plot_grob$layout$name == axisb_txt)]] <- axisb[[1]][[1]]
        pattern_txt <- paste0(panels[ch_pos$PANEL, ]$name, "|", strips[ch_pos$PANEL, ]$name)
        ch_grob <- g_filter(plot_grob, pattern_txt, trim = TRUE) %>%
            gtable::gtable_add_rows(rowsize) %>%
            gtable::gtable_add_grob(axisb[[1]][[1]], 3, 1) %>%
            gtable::gtable_add_cols(colsize, 0) %>%
            gtable::gtable_add_grob(axisl[[1]][[1]], 2, 1)

        #  #if there is no bottom axis, add one:
        #  if(is.null(g_filter(ch_grob,"axis-b")[[1]][[1]]$height)){
        #    ch_grob <- ch_grob %>%
        #     gtable::gtable_add_grob( axisb[[1]][[1]],3,2) %>%
        #     gtable::gtable_add_rows(rowsize)
        #  }
        #  if(is.null(g_filter(ch_grob,"axis-l")[[1]][[1]]$width)){
        #    ch_grob <- ch_grob %>% gtable::gtable_add_grob(axisl[[1]][[1]],2,1) %>%
        #    gtable::gtable_add_cols(colsize,0)
        # }

        ch_grob
    }) %>% stats::setNames(layout$.key)
    # #gtable::gtable_height(ch_grob)
    # grid::heightDetails(ch_grob)
    # grid::heightDetails(ch_grob)
    # ch_grob$widths
    #
    # # grid::heightDetails()
    # grid::grid.newpage()
    # grid::grid.draw(channel_grobs[[4]])
    # grid::grid.draw(ch_grob)
    #
    # Discard facet panels from the original plot:
    rest_grobs <- g_filter_out(plot_grob, "panel|strip-t|axis|xlab|ylab", trim = FALSE)

    # How much larger than the electrode position should the plot be?


    ch_location <- change_coord(ch_location, .projection)

    xmin <- min(ch_location$.x, na.rm = TRUE) - 0.3 #* size
    xmax <- max(ch_location$.x, na.rm = TRUE) + 0.3 #* size
    ymin <- min(ch_location$.y, na.rm = TRUE) - 0.3 #* size
    ymax <- max(ch_location$.y, na.rm = TRUE) + 0.3 #* size
    new_plot <- ggplot2::ggplot(
        data.frame(x = c(xmin, xmax), y = c(ymin, ymax)),
        ggplot2::aes_(x = ~x, y = ~y)
    ) +
        ggplot2::geom_blank() +
        ggplot2::scale_x_continuous(limits = c(xmin, xmax), expand = c(0, 0)) +
        ggplot2::scale_y_continuous(limits = c(ymin, ymax), expand = c(0, 0)) +
        ggplot2::theme_void() +
        ggplot2::annotation_custom(rest_grobs,
            xmin = xmin,
            xmax = xmax,
            ymin = ymin,
            ymax = ymax
        )

    for (i in seq_len(length(channel_grobs))) {
        new_coord <- ch_location %>%
            dplyr::filter(.key == names(channel_grobs)[[i]]) %>%
            dplyr::distinct(.x, .y)
        if (is.na(new_coord$.x) && is.na(new_coord$.y)) {
            new_plot
        } else if (is.na(new_coord$.x) | is.na(new_coord$.y)) {
            warning("X or Y coordinates are missing for electrode ", names(channel_grobs)[[i]])
        } else {
            new_plot <- new_plot + ggplot2::annotation_custom(channel_grobs[[i]],
                xmin = new_coord$.x - .13 * size_x,
                xmax = new_coord$.x + .13 * size_x,
                ymin = new_coord$.y - .13 * size_y,
                ymax = new_coord$.y + .13 * size_y
            )
        }
    }
    new_plot
}
```

```{r}
# filter df as only we only have layout for 32 channels
filt_df <- erp_df |>
    left_join(layout_32_1020 |> rename(".key" = .channel)) |>
    filter(!is.na(.x))
```

```{r}
reading_cond <- "SPR"
only_content_words <- FALSE

erp_facet_plot(
    df = filt_df,
    reading_cond = reading_cond,
    content_words = only_content_words
) |> plot_in_layout()

ggsave(
    file.path(
        figs_path, paste("plot_in_layout_32_", reading_cond, "_contentwords",
            only_content_words, ".png",
            sep = ""
        )
    ),
    width = 10, height = 12
)
```

## Topographic plot
```{r}
epoch_file <- list.files(
    "data/epochs/",
    full.names = TRUE,
    pattern = ".rds$"
)[1]

epochs <- readRDS(epoch_file)
```
```{r}
reading_cond <- "SPR"

# add cordinates to channels tbl
channels_tbl(epochs) <- channels_tbl(epochs) |>
    left_join(layout_32_1020)

# only choice channels with layout coordinates
layout_channels <- layout_32_1020 |>
    filter(!(.channel %in% c("M1", "M2", "HEOG", "VEOG"))) |>
    pull(.channel)

epochs |>
    eeg_filter(!is.na(lp_quantile)) |>
    eeg_select(layout_channels) |>
    eeg_filter(reading_type == reading_cond) |>
    eeg_filter(as_time(.sample) |> between(0.3, 0.5)) |>
    eeg_group_by(lp_quantile) |>
    eeg_summarize(across_ch(mean, na.rm = TRUE)) |>
    eeg_mutate(
        "lp_quantile" = case_when(
            lp_quantile == "low_lp" ~ "<25%",
            lp_quantile == "med_lp" ~ "25%-75%",
            lp_quantile == "high_lp" ~ ">75%",
        )
    ) |>
    plot_topo() +
    # add a head and nose shape
    annotate_head() +
    # add electrode labels
    annotate_electrodes(color = "black") +
    facet_grid(~ as.factor(lp_quantile, levels = c("<25%", "25%-75%", ">75%")))
```

```{r}
epochs |>
    eeg_filter(!is.na(lp_quantile)) |>
    eeg_select(layout_channels) |>
    eeg_filter(reading_type == reading_cond) |>
    eeg_filter(as_time(.sample) |> between(0.3, 0.5)) |>
    eeg_group_by(lp_quantile) |>
    eeg_summarize(across_ch(mean, na.rm = TRUE)) |>
    # eeg_interpolate_tbl() |>
    plot_topo() +
    # add a head and nose shape
    annotate_head() +
    # add electrode labels
    annotate_electrodes(color = "black") +
    facet_grid(~ as.factor(lp_quantile))
```

```{r}
plot_topo_erp <- function(data) {
    plot <-
        ggplot2::ggplot(data, ggplot2::aes(
            x = .x, y = .y,
            z = .key
        )) +
        geom_tile(aes(fill = .value)) +
        ggplot2::geom_raster(ggplot2::aes(fill = .value),
            interpolate = TRUE, hjust = 0.5, vjust = 0.5
        ) +
        # Non recommended "rainbow" Matlab palette from https://www.mattcraddock.com/blog/2017/02/25/erp-visualization-creating-topographical-scalp-maps-part-1/
        #    scale_fill_gradientn(colors = colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000")),guide = "colourbar",oob = scales::squish)+
        # Not that bad scale:
        #    scale_fill_distiller(palette = "Spectral", guide = "colorbar", oob = scales::squish) + #
        ggplot2::scale_fill_distiller(type = "div", palette = "RdBu", guide = "colorbar", oob = scales::squish) +
        theme_eeguana2()
    plot
}
```

```{r}
reading_cond <- "SPR"

erp_df |>
    filter(reading_type == reading_cond) |>
    left_join(layout_32_1020 |> rename(".key" = .channel)) |>
    filter(!is.na(.x)) |>
    mutate(
        "lp_quantile" = case_when(
            lp_quantile == "low_lp" ~ "<25%",
            lp_quantile == "med_lp" ~ "25%-75%",
            lp_quantile == "high_lp" ~ ">75%",
        )
    ) |>
    plot_topo_erp() +
    annotate_head() +
    # add electrode labels
    annotate_electrodes(color = "black") +
    facet_grid(~ factor(lp_quantile, levels = c("<25%", "25%-75%", ">75%"))) +
    theme(legend.position = "bottom")

ggsave(
    file.path(
        figs_path, paste("plot_topo_", reading_cond, ".png",
            sep = ""
        )
    ),
    width = 10, height = 7
)
```

### code with interpolation from chatgpt
Define functions
```{r}
topo_plot_quantiles <- function(df, reading_cond, content_words, timewindow) {
    # Join layout info
    plot_data <- df |>
        filter(reading_type == reading_cond) |>
        left_join(layout_32_1020 |>
            rename(".key" = .channel)) |>
        filter(!is.na(.x)) |>
        filter(.time |>
            between(timewindow[1], timewindow[2])) |>
        mutate(
            "lp_quantile" = case_when(
                lp_quantile == "low_lp" ~ "<25%",
                lp_quantile == "med_lp" ~ "25%-75%",
                lp_quantile == "high_lp" ~ ">75%",
            )
        )

    # specify content words true or false
    if (content_words) {
        plot_data <- plot_data |>
            mutate(".value" = .value_content_words)
    }

    # Group-wise interpolation
    interp_per_group <- plot_data |>
        group_split(lp_quantile) |>
        map_df(function(df) {
            group_name <- unique(df$lp_quantile)

            # Compute group mean per electrode
            mean_vals <- df |>
                group_by(.key, .x, .y) |>
                summarise(.value = mean(.value), .groups = "drop")

            # Perform interpolation
            interp <- akima::interp(
                x = mean_vals$.x,
                y = mean_vals$.y,
                z = mean_vals$.value,
                duplicate = "mean",
                nx = 100,
                ny = 100
            )

            # Make raster tibble
            raster_tbl <- expand.grid(.x = interp$x, .y = interp$y) |>
                mutate(
                    .value = as.vector(interp$z),
                    lp_quantile = group_name
                )

            # Label data for this group
            label_tbl <- mean_vals |>
                mutate(lp_quantile = group_name)

            # Combine both
            bind_rows(raster_tbl, label_tbl)
        })

    # Plot
    p <- plot_topo(as_tibble(interp_per_group)) +
        annotate_head() +
        annotate_electrodes(color = "black") +
        facet_grid(~ factor(lp_quantile, levels = c("<25%", "25%-75%", ">75%"))) +
        scale_fill_distiller(
            type = "div",
            palette = "RdBu",
            guide = "colorbar",
            oob = scales::squish,
            na.value = "white"
        ) +
        coord_fixed() +
        labs(fill = "\u03BCV") +
        theme(
            panel.background = element_rect(fill = "white", color = NA),
            plot.background = element_rect(fill = "white", color = NA),
            legend.position = "bottom"
        )

    return(p)
}

topo_plot_diff <- function(df, reading_cond, content_words, timewindow) {
    if (content_words) {
        value_col <- ".value_content_words"
        other_value_col <- ".value"
    } else {
        value_col <- ".value"
        other_value_col <- ".value_content_words"
    }


    # Your summarized data
    base_data <- df |>
        select(-X, -n_subjects, -other_value_col) |>
        filter(reading_type == reading_cond) |>
        left_join(layout_32_1020 |>
            rename(".key" = .channel)) |>
        filter(!is.na(.x)) |>
        filter(.time |>
            between(timewindow[1], timewindow[2])) |>
        pivot_wider(names_from = "lp_quantile", values_from = value_col) |>
        mutate(.value = low_lp - high_lp) |> # difference between high and low probability words
        group_by(.key, .x, .y) |>
        summarise(.value = mean(.value), .groups = "drop")

    # Interpolate to a fine grid
    interp_result <- akima::interp(
        x = base_data$.x,
        y = base_data$.y,
        z = base_data$.value,
        duplicate = "mean",
        nx = 100,
        ny = 100
    )

    # Convert interpolation result to a tibble
    interp_df <- expand.grid(
        .x = interp_result$x,
        .y = interp_result$y
    ) |>
        mutate(.value = as.vector(interp_result$z))

    # Prepare label data
    label_data <- base_data

    # Combine with NA-labeled version for compatibility with plot_topo
    plot_data_ready <- bind_rows(
        interp_df |> mutate(.key = NA),
        label_data
    )

    # Plot
    p <- plot_topo(as_tibble(plot_data_ready)) +
        annotate_head() +
        annotate_electrodes(color = "black") +
        scale_fill_distiller(
            type = "div",
            palette = "RdBu",
            guide = "colorbar",
            oob = scales::squish,
            na.value = "white"
        ) +
        coord_fixed() +
        labs(fill = "\u03BCV", caption = "Difference (< 25%) - (> 75%)") +
        theme(
            panel.background = element_rect(fill = "white", color = NA),
            plot.background = element_rect(fill = "white", color = NA),
            legend.position = "bottom"
        ) +
        theme(
            legend.position = "bottom",
            plot.caption = element_text(hjust = 0.5) # centers the caption
        )

    return(p)
}
```

One topo plot for each condition
```{r}
reading_cond <- "SPR"
content_words <- FALSE
erp_component <- "n400"

if (erp_component == "n400") {
    timewindow <- n400_timewindow
} else if (erp_component == "p600") {
    timewindow <- p600_timewindow
} else {
    timewindow <- c(min(erp_df$.time), max(erp_df$.time))
}

topo_plot_quantiles(erp_df, reading_cond, content_words, timewindow)

ggsave(
    file.path(
        figs_path, paste("plot_topo_", reading_cond, "_",
            erp_component, "_contentwords", content_words, ".png",
            sep = ""
        )
    ),
    width = 10, height = 7
)
```

topo plot of difference between conditions
```{r}
reading_cond <- "SPR"
content_words <- TRUE
erp_component <- "n400"

if (erp_component == "n400") {
    timewindow <- n400_timewindow
} else if (erp_component == "p600") {
    timewindow <- p600_timewindow
} else {
    timewindow <- c(min(erp_df$.time), max(erp_df$.time))
}

topo_plot_diff(erp_df, reading_cond, content_words, timewindow)

ggsave(
    file.path(
        figs_path, paste("plot_topo_diff_", reading_cond, "_",
            erp_component, "_contentwords", content_words, ".pdf",
            sep = ""
        )
    ),
    width = 4, height = 4
)
```

### Plot topo and ERP together
```{r}
reading_cond <- "SPR"
content_words <- TRUE
erp_component <- "n400" # only n400 and p600

if (erp_component == "n400") {
    chs <- n400_chs
    timewindow <- n400_timewindow
} else if (erp_component == "p600") {
    chs <- p600_chs
    timewindow <- p600_timewindow
}

erp_p <- erp_mean_plot(
    df = erp_df,
    reading_cond = reading_cond,
    channels = chs,
    content_words = content_words,
    annotate_timewindow = timewindow
) + theme(legend.position = "bottom")

topo_p <- topo_plot_diff(
    df = erp_df,
    reading_cond = reading_cond,
    content_words = content_words,
    timewindow = timewindow
) + theme(legend.position = "right")

(erp_p + topo_p) +
    # change alignment of caption if you change size of saved plot
    theme(plot.caption = element_text(vjust = 15, hjust = 0.9))

ggsave(
    file.path(
        figs_path, paste("erp_topo_", reading_cond, "_",
            erp_component, "_contentwords", content_words, ".pdf",
            sep = ""
        )
    ),
    width = 8, height = 4
)
```

```{r}
# for AMLaP poster
reading_cond <- "SPR"
content_words <- TRUE
erp_component <- "n400" # only n400 and p600

if (erp_component == "n400") {
    chs <- n400_chs
    timewindow <- n400_timewindow
} else if (erp_component == "p600") {
    chs <- p600_chs
    timewindow <- p600_timewindow
}

erp_p <- erp_mean_plot(
    df = erp_df,
    reading_cond = "SPR",
    channels = n400_chs,
    content_words = TRUE,
    annotate_timewindow = n400_timewindow
) + theme(legend.position = "bottom") +
    labs(
        subtitle =
            "ERPs for content words with a log-probability in different
quantiles averaged for centroparietal channels"
    )

topo_p <- topo_plot_diff(
    df = erp_df,
    reading_cond = "SPR",
    content_words = TRUE,
    timewindow = n400_timewindow
) + theme(legend.position = "right") +
    labs(
        subtitle = "Subtraction plot of the ERPs in the
time window between 300-500 ms"
    )

(erp_p + topo_p) +
    # change alignment of caption if you change size of saved plot
    theme(plot.caption = element_text(vjust = 15, hjust = 0.9))

ggsave(
    file.path(
        figs_path, paste("erp_topo_amlap.png",
            sep = ""
        )
    ),
    width = 8, height = 4
)
```
