# Results of Bayesian Hierarchical Models
```{r}
library(tidytable)
library(stringr)
library(brms)
library(ggplot2)
library(patchwork)

setwd("paper")

models_path <- file.path("src", "brms_models")
fig_path <- "figs"
```

## read models
Dependent variables (dep_var) are reading times (rt), N400 (n400), and P600 (p600).
For the two EEG models, n400 and p600, models were fit seperately for RSVP and SPR reading conditions.
Model formula 1 (m1): dep_var ~ s_lp + s_freq
Model formula 2 (m2): dep_var ~ -1 + content_word + content_word:s_lp + content_word:s_freq 
Model formula 3 (m3): dep_var ~ s_lp + s_wl + s_freq
```{r}
# dependent variable (rt, n400, or p600)
dep_var <- "p600"
# SPR or RSVP (for rt only SPR)
reading_cond <- "SPR"
# model formula (m1, m2, or m3)
model_formula <- "m1"

m <- readRDS(file.path(
    models_path,
    paste(dep_var, "_", reading_cond, "_", model_formula, ".rds", sep = "")
))
```

# Model checks
```{r}
pp_check(m)

p <- plot(m, variable = "^b", regex = TRUE)
```

## Prior-poserior update
```{r}
draws <- as.data.frame(m)
```

Beta coefficients
```{r}
draws |>
    pivot_longer(
        cols = starts_with("b_s"),
        names_to = "parameter", values_to = "posterior"
    ) |>
    rename("prior" = prior_b) |>
    select(posterior, prior, parameter) |>
    ggplot() +
    geom_density(aes(x = prior), fill = "steelblue1", alpha = .5) +
    geom_density(aes(x = posterior), fill = "firebrick", alpha = .5) +
    facet_wrap(. ~ parameter) +
    theme_bw()
```

Intercept
```{r}
p <- draws |>
    rename(
        "prior" = prior_Intercept,
        "posterior" = b_Intercept
    ) |>
    ggplot() +
    geom_density(aes(x = prior), fill = "steelblue1", alpha = .5) +
    geom_density(aes(x = posterior), fill = "firebrick", alpha = .5) +
    theme_bw()
ggsave(
    file.path(
        fig_path,
        paste(model_formula, "_pp_intercept.png", sep = "")
    ),
    p
)
```

Intercept
```{r}
draws |>
    rename(
        "prior" = prior_Intercept,
        "posterior" = b_Intercept
    ) |>
    ggplot() +
    geom_density(aes(x = prior), fill = "steelblue1", alpha = .5) +
    geom_density(aes(x = posterior), fill = "steelblue3", alpha = .5) +
    theme_minimal()
```

### Only priors
```{r}
draws |>
    pivot_longer(
        cols = starts_with("prior_"),
        names_to = "parameter", values_to = "prior"
    ) |>
    mutate("parameter" = str_remove(parameter, "^prior_")) |>
    select(parameter, prior) |>
    ggplot() +
    geom_density(aes(x = prior), fill = "steelblue3", alpha = .5) +
    facet_wrap(. ~ parameter) +
    theme_minimal()
```

# results
```{r}
summary(m)

mcmc_plot(m, variable = "^b", regex = TRUE)
```

# plot of fixed effects
```{r}
if (exists("fixef_all")) {
    rm(fixef_all)
}

for (dep_var in c("rt", "n400", "p600")) {
    for (reading_cond in c("RSVP", "SPR")) {
        if (dep_var == "rt" && reading_cond == "RSVP") {
            next
        }

        m <- readRDS(file.path(
            models_path,
            paste(
                dep_var, "_",
                reading_cond, "_",
                "m1.rds",
                sep = ""
            )
        ))

        fixef_m <- fixef(m) |>
            as.data.frame() |>
            mutate(
                "estimate_name" = c(
                    "Intercept",
                    "Log-\nprobability",
                    "Zipf \nfrequency"
                ),
                "dependent_variable" = dep_var,
                "reading_condition" = reading_cond
            )

        if (exists("fixef_all")) {
            fixef_all <- rbind(fixef_all, fixef_m)
        } else {
            fixef_all <- fixef_m
        }
    }
}
```

```{r}
plot_fixef <- function(df, scale) {
    dodge <- position_dodge(width = 0.3)

    p <- ggplot(df, aes(y = estimate_name, color = reading_condition)) +
        geom_vline(aes(xintercept = 0), linetype = "dashed") +
        geom_point(aes(x = Estimate), position = dodge) +
        geom_linerange(aes(xmin = Q2.5, xmax = Q97.5),
            position = dodge
        ) +
        scale_color_manual(values = c("steelblue4", "steelblue1")) +
        labs(color = "", y = "", x = scale) +
        theme_minimal() +
        theme(legend.position = "bottom")

    return(p)
}
```

```{r}
dodge <- position_dodge(width = 0.3)

fixef_plot <- fixef_all |>
    filter(estimate_name != "Intercept") |>
    mutate(reading_condition = factor(
        reading_condition,
        levels = c("SPR", "RSVP")
    ))

n400_p <- fixef_plot |>
    filter(dependent_variable == "n400") |>
    plot_fixef(scale = "\u03BCV") +
    labs(title = "N400")

p600_p <- fixef_plot |>
    filter(dependent_variable == "p600") |>
    plot_fixef(scale = "\u03BCV") +
    labs(title = "P600")

rt_p <- fixef_plot |>
    filter(dependent_variable == "rt") |>
    ggplot(aes(y = estimate_name)) +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    geom_point(aes(x = Estimate), position = dodge) +
    geom_linerange(aes(xmin = Q2.5, xmax = Q97.5),
        position = dodge
    ) +
    scale_color_manual(values = c("steelblue4")) +
    labs(color = "", y = "", x = "ms") +
    theme_minimal() +
    theme(legend.position = "bottom") +
    labs(title = "Reading Times")

(n400_p + p600_p + rt_p) +
    plot_layout(guides = "collect", axes = "collect_y") &
    theme(
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5, size = 10)
    )

ggsave("figs/regression_coefficients.pdf", height = 3, width = 6)
```