# Results of Bayesian Hierarchical Models
```{r}
library(tidytable)
library(stringr)
library(brms)
library(priorsense)
library(ggplot2)

setwd("paper")

models_path <- file.path("src", "brms_models")
fig_path <- "figs"
```

## read models
Dependent variables (dep_var) are reading times (rt), N400 (n400), and P600 (p600).
For the two EEG models, n400 and p600, models were fit seperately for RSVP and SPR reading conditions.
Model formula 1 (m1): dep_var ~ s_lp + s_freq
Model formula 2 (m2): dep_var ~ -1 + content_word + content_word:s_lp + content_word:s_freq 
Model formula 3 (m3): dep_var ~ s_lp + s_wl + s_freq
```{r}
# dependent variable (rt, n400, or p600)
dep_var <- "n400"
# SPR or RSVP (for rt only SPR)
reading_cond <- "SPR"
# model formula (m1, m2, or m3)
model_formula <- "m1"

m <- readRDS(file.path(
    models_path,
    paste(dep_var, "_", reading_cond, "_", model_formula, ".rds", sep = "")
))
```

# Model checks
```{r}
pp_check(m)

p <- plot(m, variable = "^b", regex = TRUE)
```

```{r}
powerscale_sensitivity(m) # check priors
```

## Prior-posterior update
```{r}
draws <- as.data.frame(m)
```

Beta coefficients
```{r}
draws |>
    pivot_longer(
        cols = starts_with("b_s"),
        names_to = "parameter", values_to = "posterior"
    ) |>
    rename("prior" = prior_b) |>
    select(posterior, prior, parameter) |>
    ggplot() +
    geom_density(aes(x = prior), fill = "steelblue1", alpha = .5) +
    geom_density(aes(x = posterior), fill = "firebrick", alpha = .5) +
    facet_wrap(. ~ parameter) +
    theme_bw()
```

Intercept
```{r}
p <- draws |>
    rename(
        "prior" = prior_Intercept,
        "posterior" = b_Intercept
    ) |>
    ggplot() +
    geom_density(aes(x = prior), fill = "steelblue1", alpha = .5) +
    geom_density(aes(x = posterior), fill = "firebrick", alpha = .5) +
    theme_bw()
ggsave(
    file.path(
        fig_path,
        paste(model_formula, "_pp_intercept.png", sep = "")
    ),
    p
)
```

Intercept
```{r}
draws |>
    rename(
        "prior" = prior_Intercept,
        "posterior" = b_Intercept
    ) |>
    ggplot() +
    geom_density(aes(x = prior), fill = "steelblue1", alpha = .5) +
    geom_density(aes(x = posterior), fill = "steelblue3", alpha = .5) +
    theme_minimal()
```

### Only priors
```{r}
draws |>
    pivot_longer(
        cols = starts_with("prior_"),
        names_to = "parameter", values_to = "prior"
    ) |>
    mutate("parameter" = str_remove(parameter, "^prior_")) |>
    select(parameter, prior) |>
    ggplot() +
    geom_density(aes(x = prior), fill = "steelblue3", alpha = .5) +
    facet_wrap(. ~ parameter) +
    theme_minimal()
```

# results
```{r}
summary(m)

mcmc_plot(m, variable = "^b", regex = TRUE)
```