# Results from single-trial ERPs (STERPs)
Single trial ERP signal generated using weights from single value decomposition of the epochs. The methods is used in [Nunez et al., 2017](https://doi.org/10.1016/j.jmp.2016.03.003). 

```{r}
library(tidytable)
library(ggplot2)
library(lmerTest)

setwd("paper")
```

## Create files
```{r}
# sterp files
sterp_files <- list.files(
    file.path("data", "sterps"),
    full.names = TRUE,
    pattern = "^sterp\\d{2}\\.csv$"
)

# create reject_df
# percent of rejected artifacts in one story for the entire story to be rejected
artifact_threshold <- .3
# reject reading times that are below or above (in ms)
rt_threshold <- c(100, 3000)

reject_df <- read.csv("data/mean_amplitude.csv") |>
    filter(document_id < 10) |> # exclude practice texts
    filter(!is.na(lp_quantile)) |>
    group_by(participant_number, document_id) |>
    summarize(
        "reject" = case_when(
            # if proportion of rejected epochs are over the threshold
            (sum(is.na(n400)) / n()) > artifact_threshold ~ TRUE,
            # reject document 1 from participant 17 (error while reading)
            (participant_number == 17 & document_id == 1) ~ TRUE,
            # reject participant 64 (problems during data collection)
            participant_number == 64 ~ TRUE,
            .default = FALSE
        )
    )

# content words
content_words <- c("NOUN", "VERB", "ADJ", "ADV")

# interesting time window
time_windows <- list(
    "early" = c(0.05, 0.08, "slategray4"),
    "p1" = c(0.08, 0.12, "darkseagreen"),
    "n1" = c(0.16, 0.2, "slategray4")
)
```

Calculate mean amplitudes in time time_windows
```{r}
for (sterp_file in sterp_files) {
    print(sterp_file)

    # read rt_df
    n <- as.numeric(gsub(".*?([0-9]+).*", "\\1", sterp_file))
    rt_df <- read_rt_participant(n)

    indv_sterps_mean <- read.csv(sterp_file) |>
        select(-X) |>
        left_join(rt_df,
            by = c(
                "segment", "participant_number",
                "document_id", "number_word"
            )
        ) |>
        filter(document_id < 10) |> # remove pratice texts
        left_join(reject_df,
            by = c("participant_number", "document_id")
        ) |>
        filter(!reject) |>
        # filter based on reject rt
        mutate(rt = reaction_time / 0.001) |> # reading times in ms instead of s
        filter(rt > rt_threshold[1] & rt < rt_threshold[2]) |>
        group_by(-.value, -.sample, -.time) |>
        summarize(
            "early" = mean(
                .value[(.time > as.numeric(time_windows$early[1]) &
                    .time < as.numeric(time_windows$early[2]))],
                na.rm = TRUE
            ),
            "p1" = mean(
                .value[(.time > as.numeric(time_windows$p1[1]) &
                    .time < as.numeric(time_windows$p1[2]))],
                na.rm = TRUE
            ),
            "n1" = mean(
                .value[(.time > as.numeric(time_windows$n1[1]) &
                    .time < as.numeric(time_windows$n1[2]))],
                na.rm = TRUE
            )
        )

    if (exists("sterp_early_df")) {
        sterp_early_df <- rbind(sterp_early_df, indv_sterps_mean)
    } else {
        sterp_early_df <- indv_sterps_mean
    }
}

write.csv(sterp_early_df, "data/sterps/sterp_early.csv")
```


Make file with average in low, med, and high lp
```{r}
## define functions
mean_sterps <- function(sterps, reading_cond) {
    mean_sterps_ <- sterps |>
        filter(reading_type == reading_cond) |>
        group_by(.time, lp_quantile) |>
        summarize(
            ".value" = mean(.value, na.rm = TRUE),
            ".value_content_words" = mean(
                .value[pos %in% content_words],
                na.rm = TRUE
            )
        ) |>
        mutate("reading_type" = reading_cond)
    return(mean_sterps_)
}

# from src/summarize_erps
update_erp_df <- function(cur_df, new_df) {
    new_df <- new_df |>
        rename(
            "value_new" = .value,
            "value_cw_new" = .value_content_words
        ) |>
        mutate("n_subjects_new" = 1)

    updated_df <- cur_df |>
        left_join(new_df) |>
        rowwise() |>
        mutate(
            ".value" = sum(.value, value_new, na.rm = TRUE),
            ".value_content_words" = sum(
                .value_content_words,
                value_cw_new,
                na.rm = TRUE
            ),
            "n_subjects" = sum(n_subjects, n_subjects_new, na.rm = TRUE)
        ) |>
        select(-value_new, -value_cw_new, -n_subjects_new)

    return(updated_df)
}
```

```{r}
# loop over files
for (sterp_file in sterp_files) {
    print(sterp_file)

    # read rt_df
    n <- as.numeric(gsub(".*?([0-9]+).*", "\\1", sterp_file))
    rt_df <- read_rt_participant(n)

    sterps <- read.csv(sterp_file) |>
        select(-X) |>
        left_join(rt_df,
            by = c(
                "segment", "participant_number",
                "document_id", "number_word"
            )
        ) |>
        filter(document_id < 10) |> # remove pratice texts
        filter(!is.na(lp_quantile)) |> # remove words with out lp value
        left_join(reject_df,
            by = c("participant_number", "document_id")
        ) |>
        filter(!reject) |>
        # filter based on reject rt
        mutate(rt = reaction_time / 0.001) |> # reading times in ms instead of s
        filter(rt > rt_threshold[1] & rt < rt_threshold[2])

    sterp_lp_spr <- mean_sterps(sterps, reading_cond = "SPR")
    sterp_lp_rsvp <- mean_sterps(sterps, reading_cond = "RSVP")
    tmp_sterp <- rbind(sterp_lp_spr, sterp_lp_rsvp)

    # save for return
    if (exists("sterp_df")) {
        sterp_df <- update_erp_df(sterp_df, tmp_sterp)
    } else {
        sterp_df <- tmp_sterp |>
            mutate("n_subjects" = 1)
    }
}

# calculate mean over all participants
sterp_df <- sterp_df |>
    mutate(
        ".value" = .value / n_subjects,
        ".value_content_words" = .value_content_words / n_subjects
    )

write.csv(sterp_df, "data/sterps/sterp_lp.csv")

# rm tmp
rm(tmp_sterp)
```

## Explore signal
Use only first 40 participants
```{r}
sterp_early_df <- read.csv("data/sterps/sterp_early.csv") |>
    filter(participant_number < 43)
sterp_df <- read.csv("data/sterps/sterp_lp.csv") |>
    filter(participant_number < 43)
```

Plots
```{r}
p <- sterp_df |>
    mutate(lp_quantile_factor = factor(
        lp_quantile,
        levels = c("low_lp", "med_lp", "high_lp")
    )) |>
    ggplot(aes(x = .time, y = .value)) +
    stat_summary(
        fun = "mean", geom = "line", alpha = 1, linewidth = 1,
        aes(color = lp_quantile_factor)
    ) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    eeguana::theme_eeguana() +
    theme(legend.position = "bottom") +
    labs(color = "", y = "") +
    scale_color_manual(values = c("steelblue1", "steelblue3", "steelblue4")) +
    xlim(-0.2, 0.4)

for (annotate_timewindow in time_windows) {
    p <- p + annotate("rect",
        xmin = as.numeric(annotate_timewindow[1]),
        xmax = as.numeric(annotate_timewindow[2]),
        ymin = -Inf, ymax = Inf,
        alpha = .2, fill = annotate_timewindow[3]
    )
}

p
```

Models
```{r}
reading_cond <- "SPR"

lp_early_m <- lmer(
    (early ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

lp_p1_m <- lmer(
    (p1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

lp_n1_m <- lmer(
    (n1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)
```

```{r}
summary(lp_early_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (early ~ s_lp + (s_lp | participant_number) + (s_lp | word) +  
    (s_lp | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 738921.9

Scaled residuals: 
    Min      1Q  Median      3Q     Max 
-7.5170 -0.6052 -0.0050  0.6027  8.7948 

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 1.252e+00  1.1188       
                    s_lp        1.682e-01  0.4101  -1.00
 participant_number (Intercept) 9.279e+01  9.6325
                    s_lp        2.438e-01  0.4938  1.00
 document_id        (Intercept) 1.706e+00  1.3061
                    s_lp        1.006e-02  0.1003  1.00 
 Residual                       3.152e+03 56.1393       
Number of obs: 67817, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)   1.2225     1.8711 31.3308   0.653    0.518
s_lp          0.2848     0.2582 69.8447   1.103    0.274

Correlation of Fixed Effects:
     (Intr)
s_lp 0.378
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(lp_p1_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |  
    document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 743314.1

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-9.3814 -0.6021 -0.0028  0.5998 10.9449 

Random effects:
 Groups             Name        Variance  Std.Dev. Corr 
 word               (Intercept) 2.402e+00  1.5497       
                    s_lp        3.364e-01  0.5800  -1.00
 participant_number (Intercept) 1.968e+02 14.0273
                    s_lp        5.827e+00  2.4139  -0.24
 document_id        (Intercept) 1.419e+00  1.1914
                    s_lp        1.608e-02  0.1268  1.00
 Residual                       3.359e+03 57.9542
Number of obs: 67817, groups:  
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)  
(Intercept)  -1.7212     2.6571 29.3521  -0.648   0.5222
s_lp          1.0847     0.5379 25.9541   2.017   0.0542 .
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp -0.185
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')


```{r}
summary(lp_n1_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |
    document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 755207.8

Scaled residuals:
     Min       1Q   Median       3Q      Max 
-10.0800  -0.5940   0.0001   0.5907  13.7173

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept)   14.7802  3.8445
                    s_lp           1.6241  1.2744  -1.00
 participant_number (Intercept)  248.0735 15.7504
                    s_lp           6.2431  2.4986  0.24
 document_id        (Intercept)    0.5037  0.7097       
                    s_lp           0.1242  0.3524  1.00 
 Residual                       3992.6115 63.1871
Number of obs: 67817, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)  -6.4606     2.9578 28.3191  -2.184   0.0374 *
s_lp         -0.4117     0.5903 31.2428  -0.697   0.4907  
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp 0.208 
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
reading_cond <- "SPR"

lp_early_content_m <- lmer(
    (early ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |>
        filter(reading_type == reading_cond) |>
        filter(pos %in% content_words)
)

lp_p1_content_m <- lmer(
    (p1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |>
        filter(reading_type == reading_cond) |>
        filter(pos %in% content_words)
)

lp_n1_content_m <- lmer(
    (n1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |>
        filter(reading_type == reading_cond) |>
        filter(pos %in% content_words)
)
```

```{r}
summary(lp_early_content_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (early ~ s_lp + (s_lp | participant_number) + (s_lp | word) +
    (s_lp | document_id))
   Data: filter(filter(sterp_early_df, reading_type == reading_cond),
    pos %in% content_words)

REML criterion at convergence: 359073.2

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-6.4033 -0.6057 -0.0101  0.5987  8.8069

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 7.609e-03  0.08723      
                    s_lp        1.264e-04  0.01124 0.82
 participant_number (Intercept) 8.883e+01  9.42519
                    s_lp        1.452e-01  0.38108 1.00
 document_id        (Intercept) 1.588e+00  1.26030      
                    s_lp        1.117e-03  0.03343 -1.00
 Residual                       3.132e+03 55.96245
Number of obs: 32972, groups:
word, 1640; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)
(Intercept)   1.2155     1.8551  31.1472   0.655    0.517
s_lp          0.1158     0.3163 275.3088   0.366    0.715

Correlation of Fixed Effects:
     (Intr)
s_lp 0.269
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(lp_p1_content_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |  
    document_id))
   Data: filter(filter(sterp_early_df, reading_type == reading_cond),  
    pos %in% content_words)

REML criterion at convergence: 361470

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-7.2993 -0.6030 -0.0015  0.5938 10.8650

Random effects:
 Groups             Name        Variance  Std.Dev. Corr 
 word               (Intercept)    2.5662  1.6019
                    s_lp           1.5436  1.2424  -0.03
 participant_number (Intercept)  235.8465 15.3573       
                    s_lp           0.7982  0.8934  -0.28
 document_id        (Intercept)    1.8249  1.3509
                    s_lp           0.0610  0.2470  1.00
 Residual                       3360.4895 57.9697       
Number of obs: 32972, groups:
word, 1640; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)  -2.3723     2.9262 29.3684  -0.811   0.4241  
s_lp          0.7169     0.3901 20.5638   1.838   0.0806 .
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp -0.038
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(lp_n1_content_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |  
    document_id))
   Data: filter(filter(sterp_early_df, reading_type == reading_cond),  
    pos %in% content_words)

REML criterion at convergence: 367175.8

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-7.8291 -0.5964 -0.0024  0.5875 13.7354

Random effects:
 Groups             Name        Variance  Std.Dev. Corr 
 word               (Intercept) 1.270e+01  3.56319
                    s_lp        1.710e+00  1.30759 -1.00
 participant_number (Intercept) 2.393e+02 15.46955
                    s_lp        1.626e-01  0.40322 0.98
 document_id        (Intercept) 8.306e-02  0.28820
                    s_lp        4.528e-03  0.06729 1.00
 Residual                       3.986e+03 63.13203
Number of obs: 32972, groups:  
word, 1640; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)
(Intercept) -5.94391    2.91385 27.57511  -2.040    0.051 .
s_lp        -0.02982    0.38268 26.53304  -0.078    0.938  
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp 0.238
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

Freq and p1
```{r}
reading_cond <- "SPR"

freq_p1_m1 <- lmer(
    (p1 ~ s_lp + s_freq +
        (s_lp + s_freq | participant_number) +
        (s_lp | word) +
        (s_lp + s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

freq_p1_m2 <- lmer(
    (p1 ~ s_lp * s_freq +
        (s_lp * s_freq | participant_number) +
        (s_lp | word) +
        (s_lp * s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)
```

```{r}
summary(freq_p1_m1)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp + s_freq + (s_lp + s_freq | participant_number) +  
    (s_lp | word) + (s_lp + s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 743270.4

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-9.3880 -0.6023 -0.0032  0.5989 10.9746

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 2.370e+00  1.5396
                    s_lp        3.935e-01  0.6273  -1.00
 participant_number (Intercept) 1.968e+02 14.0289
                    s_lp        1.810e+00  1.3455  -0.05
                    s_freq      3.478e+00  1.8650  -0.41  0.93
 document_id        (Intercept) 1.407e+00  1.1862
                    s_lp        1.253e-02  0.1119  -0.12
                    s_freq      3.096e-01  0.5564   0.59 -0.87
 Residual                       3.356e+03 57.9312
Number of obs: 67817, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)  
(Intercept)  -1.7084     2.6570 29.2884  -0.643    0.525
s_lp          0.9416     0.3940 31.5901   2.390    0.023 *
s_freq        0.1520     0.4995 12.6231   0.304    0.766
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr) s_lp
s_lp   -0.035
s_freq -0.235  0.197
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(freq_p1_m2)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp * s_freq + (s_lp * s_freq | participant_number) +
    (s_lp | word) + (s_lp * s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 743259.5

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-9.3877 -0.6031 -0.0034  0.5996 10.9571 

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept)    2.4854  1.5765
                    s_lp           0.4194  0.6476  -0.99
 participant_number (Intercept)  197.0911 14.0389
                    s_lp           4.7183  2.1722  -0.06
                    s_freq         2.4762  1.5736  -0.50  0.90
                    s_lp:s_freq    0.8981  0.9477  -0.06  1.00  0.89
 document_id        (Intercept)    1.6266  1.2754
                    s_lp           0.1773  0.4210  -0.52
                    s_freq         0.5035  0.7096   0.61 -0.99      
                    s_lp:s_freq    0.1329  0.3646  -0.68  0.98 -1.00
 Residual                       3355.2492 57.9245
Number of obs: 67817, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)  -1.6986     2.6681 29.4770  -0.637    0.529
s_lp          0.9435     0.5890 21.7774   1.602    0.124
s_freq        0.1745     0.4953  9.6931   0.352    0.732
s_lp:s_freq   0.0108     0.3669 15.9170   0.029    0.977

Correlation of Fixed Effects:
            (Intr) s_lp   s_freq
s_lp        -0.092
s_freq      -0.224  0.037
s_lp:s_freq -0.113  0.781 -0.051
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

Freq and n1
```{r}
reading_cond <- "SPR"

freq_n1_m <- lmer(
    (n1 ~ s_freq +
        (s_freq | participant_number) +
        (s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

freq_n1_m1 <- lmer(
    (n1 ~ s_lp + s_freq +
        (s_lp + s_freq | participant_number) +
        (s_lp | word) +
        (s_lp + s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

freq_n1_m2 <- lmer(
    (n1 ~ s_lp * s_freq +
        (s_lp * s_freq | participant_number) +
        (s_lp | word) +
        (s_lp * s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)
```

```{r}
summary(freq_n1_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_freq + (s_freq | participant_number) + (s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 755977.3

Scaled residuals: 
     Min       1Q   Median       3Q      Max 
-10.0270  -0.5944  -0.0006   0.5891  13.7846

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 participant_number (Intercept) 2.449e+02 15.65067
                    s_freq      1.865e+01  4.31835 0.43
 document_id        (Intercept) 6.578e-01  0.81103
                    s_freq      8.698e-03  0.09326 1.00
 Residual                       3.993e+03 63.19246
Number of obs: 67903, groups:  participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)  -7.1713     2.9378 28.2875  -2.441   0.0212 *
s_freq       -2.2082     0.8535 27.8025  -2.587   0.0152 *
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr)
s_freq 0.404
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(freq_n1_m1)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp + s_freq + (s_lp + s_freq | participant_number) +
    (s_lp | word) + (s_lp + s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 754987.1

Scaled residuals: 
     Min       1Q   Median       3Q      Max
-10.0429  -0.5939  -0.0010   0.5891  13.7706 

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 7.308e+00  2.70327
                    s_lp        2.683e+00  1.63791 -1.00
 participant_number (Intercept) 2.471e+02 15.72002
                    s_lp        1.129e+00  1.06276 -0.32
                    s_freq      1.833e+01  4.28139  0.46 -0.14
 document_id        (Intercept) 6.045e-01  0.77751
                    s_lp        1.428e-01  0.37782  1.00
                    s_freq      8.824e-06  0.00297 -1.00 -1.00
 Residual                       3.982e+03 63.10658
Number of obs: 67817, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)  -7.0943     2.9519 28.2321  -2.403   0.0231 *
s_lp          0.4901     0.4189 15.6307   1.170   0.2595
s_freq       -2.3532     0.8707 28.2398  -2.703   0.0115 *
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr) s_lp
s_lp   -0.125
s_freq  0.423 -0.209
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(freq_n1_m2)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp * s_freq + (s_lp * s_freq | participant_number) +
    (s_lp | word) + (s_lp * s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 754983.7

Scaled residuals:
     Min       1Q   Median       3Q      Max 
-10.0426  -0.5931  -0.0010   0.5888  13.7702

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 7.107e+00  2.66597
                    s_lp        2.655e+00  1.62956 -1.00
 participant_number (Intercept) 2.514e+02 15.85713
                    s_lp        1.784e+00  1.33550 -0.44
                    s_freq      1.748e+01  4.18032  0.48  0.06
                    s_lp:s_freq 3.343e-01  0.57819 -0.52  0.68  0.47
 document_id        (Intercept) 5.832e-01  0.76365
                    s_lp        1.775e-01  0.42130  1.00
                    s_freq      3.047e-04  0.01746 -1.00 -1.00
                    s_lp:s_freq 1.025e-03  0.03201  1.00  1.00 -1.00
 Residual                       3.982e+03 63.10649
Number of obs: 67817, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)
(Intercept)  -7.0222     2.9808  28.2254  -2.356   0.0257 *
s_lp          0.3499     0.5232  18.5935   0.669   0.5119
s_freq       -2.2870     0.8575  27.8501  -2.667   0.0126 *
s_lp:s_freq  -0.1811     0.3441 132.2183  -0.526   0.5996
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
            (Intr) s_lp   s_freq
s_lp        -0.213
s_freq       0.439 -0.148
s_lp:s_freq -0.209  0.595  0.036
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

## Confirmatory analysis
```{r}
sterp_early_df <- read.csv("data/sterps/sterp_early.csv") |>
    filter(participant_number >= 43)
```

P1 models
```{r}
reading_cond <- "SPR"

lp_p1_m <- lmer(
    (p1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

freq_p1_m1 <- lmer(
    (p1 ~ s_lp + s_freq +
        (s_lp + s_freq | participant_number) +
        (s_lp | word) +
        (s_lp + s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)
```

```{r}
summary(lp_p1_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |
    document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 618420.8

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-7.6054 -0.6231 -0.0034  0.6152 11.0382 

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 1.877e-01  0.4333
                    s_lp        1.905e+00  1.3802  -1.00
 participant_number (Intercept) 1.092e+02 10.4499
                    s_lp        7.255e+00  2.6934  -0.37
 document_id        (Intercept) 3.535e-01  0.5946
                    s_lp        6.622e-02  0.2573  0.55
 Residual                       3.836e+03 61.9322
Number of obs: 55750, groups:
word, 1975; participant_number, 24; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)   
(Intercept)  -7.8734     2.1644 23.5186  -3.638  0.00134 **
s_lp         -0.1977     0.6405 18.5056  -0.309  0.76103
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp -0.307
optimizer (nloptwrap) convergence code: 0 (OK)
Model failed to converge with max|grad| = 0.00450416 (tol = 0.002, component 1)

```{r}
summary(freq_p1_m1)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp + s_freq + (s_lp + s_freq | participant_number) +  
    (s_lp | word) + (s_lp + s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 618381.8

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-7.6265 -0.6224 -0.0027  0.6151 10.9837

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept)    0.0000  0.0000
                    s_lp           1.4340  1.1975   NaN
 participant_number (Intercept)  108.8609 10.4336
                    s_lp           2.1737  1.4743  -0.33
                    s_freq         4.8434  2.2008  -0.41  1.00
 document_id        (Intercept)    0.3285  0.5732
                    s_lp           0.1802  0.4245   0.68      
                    s_freq         0.0172  0.1311  -0.35 -0.93
 Residual                       3832.9425 61.9108
Number of obs: 55750, groups:
word, 1975; participant_number, 24; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)  -7.9264     2.1608 23.5253  -3.668  0.00124 **
s_lp         -0.0159     0.4835 11.8964  -0.033  0.97431
s_freq       -0.2632     0.5579 23.4936  -0.472  0.64149
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr) s_lp
s_lp   -0.184
s_freq -0.325  0.283
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

N1 and frequency
```{r}
reading_cond <- "SPR"

freq_n1_m <- lmer(
    (n1 ~ s_freq +
        (s_freq | participant_number) +
        (s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)
```

```{r}
summary(freq_n1_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_freq + (s_freq | participant_number) + (s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 629955.6

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-9.8136 -0.6132 -0.0057  0.6044 13.3855

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 participant_number (Intercept)  234.4292 15.3111
                    s_freq        14.1977  3.7680  0.23
 document_id        (Intercept)    1.6405  1.2808
                    s_freq         0.1258  0.3547  -1.00
 Residual                       4642.0453 68.1326
Number of obs: 55829, groups:  participant_number, 24; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)  -6.2421     3.1755 23.9653  -1.966    0.061 .
s_freq       -0.9180     0.8412 23.3343  -1.091    0.286
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr)
s_freq 0.186
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')