# Results from single-trial ERPs (STERPs)
Single trial ERP signal generated using weights from single value decomposition of the epochs. The methods is used in [Nunez et al., 2017](https://doi.org/10.1016/j.jmp.2016.03.003). 

```{r}
library(tidytable)
library(ggplot2)
library(lmerTest)

setwd("paper")
```

```{r}
# sterp files
sterp_files <- list.files(
    file.path("data", "sterps"),
    full.names = TRUE,
    pattern = ".csv$"
)

# create reject_df
artifact_threshold <- .3

reject_df <- read.csv("data/mean_amplitude.csv") |>
    filter(document_id < 10) |> # exclude practice texts
    filter(!is.na(lp_quantile)) |>
    group_by(participant_number, document_id) |>
    summarize(
        "reject" = ifelse(
            # if proportion of rejected epochs are under the threshold
            (sum(is.na(n400)) / n()) < artifact_threshold,
            FALSE, TRUE
        )
    ) |>
    mutate(
        "reject" = ifelse(
            # reject document 1 from participant 17 (error while reading)
            # and remove participant 64 (problems during data collection)
            ((participant_number == 17 & document_id == 1) |
                participant_number == 64),
            TRUE, reject
        )
    )

# content words
content_words <- c("NOUN", "VERB", "ADJ", "ADV")

# interesting time window
time_windows <- list(
    "early" = c(0.05, 0.08, "slategray4"),
    "p1" = c(0.08, 0.12, "darkseagreen"),
    "n1" = c(0.16, 0.2, "slategray4")
)
```


## Explore signal
Make file with average in low, med, and high lp
```{r}
## define functions
mean_sterps <- function(sterps, reading_cond) {
    mean_sterps_ <- sterps |>
        filter(reading_type == reading_cond) |>
        group_by(.time, lp_quantile) |>
        summarize(
            ".value" = mean(.value, na.rm = TRUE),
            ".value_content_words" = mean(
                .value[pos %in% content_words],
                na.rm = TRUE
            )
        ) |>
        mutate("reading_type" = reading_cond)
    return(mean_sterps_)
}

# from src/summarize_erps
update_erp_df <- function(cur_df, new_df) {
    new_df <- new_df |>
        rename(
            "value_new" = .value,
            "value_cw_new" = .value_content_words
        ) |>
        mutate("n_subjects_new" = 1)

    updated_df <- cur_df |>
        left_join(new_df) |>
        rowwise() |>
        mutate(
            ".value" = sum(.value, value_new, na.rm = TRUE),
            ".value_content_words" = sum(
                .value_content_words,
                value_cw_new,
                na.rm = TRUE
            ),
            "n_subjects" = sum(n_subjects, n_subjects_new, na.rm = TRUE)
        ) |>
        select(-value_new, -value_cw_new, -n_subjects_new)

    return(updated_df)
}
```

```{r}
# loop over files
for (sterp_file in sterp_files) {
    print(sterp_file)

    sterps <- read.csv(sterp_file) |>
        select(-X) |>
        filter(document_id < 10) |> # remove pratice texts
        filter(!is.na(lp_quantile)) |> # remove words with out lp value
        left_join(reject_df,
            by = c("participant_number", "document_id")
        ) |>
        filter(!reject)

    sterp_lp_spr <- mean_sterps(sterps, reading_cond = "SPR")
    sterp_lp_rsvp <- mean_sterps(sterps, reading_cond = "RSVP")
    tmp_sterp <- rbind(sterp_lp_spr, sterp_lp_rsvp)

    # save for return
    if (exists("sterp_df")) {
        sterp_df <- update_erp_df(sterp_df, tmp_sterp)
    } else {
        sterp_df <- tmp_sterp |>
            mutate("n_subjects" = 1)
    }
}

# calculate mean over all participants
sterp_df <- sterp_df |>
    mutate(
        ".value" = .value / n_subjects,
        ".value_content_words" = .value_content_words / n_subjects
    )

# rm tmp
rm(tmp_sterp)
```

Plots
```{r}
p <- sterp_df |>
    mutate(lp_quantile_factor = factor(
        lp_quantile,
        levels = c("low_lp", "med_lp", "high_lp")
    )) |>
    ggplot(aes(x = .time, y = .value)) +
    stat_summary(
        fun = "mean", geom = "line", alpha = 1, linewidth = 1,
        aes(color = lp_quantile_factor)
    ) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    eeguana::theme_eeguana() +
    theme(legend.position = "bottom") +
    labs(color = "", y = "") +
    scale_color_manual(values = c("steelblue1", "steelblue3", "steelblue4")) +
    xlim(-0.2, 0.4)

for (annotate_timewindow in time_windows) {
    p <- p + annotate("rect",
        xmin = as.numeric(annotate_timewindow[1]),
        xmax = as.numeric(annotate_timewindow[2]),
        ymin = -Inf, ymax = Inf,
        alpha = .2, fill = annotate_timewindow[3]
    )
}

p
```

## Model signal
Calculate mean amplitudes in time time_windows
```{r}
for (sterp_file in sterp_files) {
    print(sterp_file)

    indv_sterps_mean <- read.csv(sterp_file) |>
        select(-X) |>
        filter(document_id < 10) |> # remove pratice texts
        left_join(reject_df,
            by = c("participant_number", "document_id")
        ) |>
        filter(!reject) |>
        group_by(-.value, -.sample, -.time) |>
        summarize(
            "early" = mean(
                .value[(.time > as.numeric(time_windows$early[1]) &
                    .time < as.numeric(time_windows$early[2]))],
                na.rm = TRUE
            ),
            "p1" = mean(
                .value[(.time > as.numeric(time_windows$p1[1]) &
                    .time < as.numeric(time_windows$p1[2]))],
                na.rm = TRUE
            ),
            "n1" = mean(
                .value[(.time > as.numeric(time_windows$n1[1]) &
                    .time < as.numeric(time_windows$n1[2]))],
                na.rm = TRUE
            )
        )

    if (exists("sterp_early_df")) {
        sterp_early_df <- rbind(sterp_early_df, indv_sterps_mean)
    } else {
        sterp_early_df <- indv_sterps_mean
    }
}
```

```{r}
reading_cond <- "SPR"

lp_early_m <- lmer(
    (early ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

lp_p1_m <- lmer(
    (p1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

lp_n1_m <- lmer(
    (n1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)
```

```{r}
summary(lp_early_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (early ~ s_lp + (s_lp | participant_number) + (s_lp | word) +
    (s_lp | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 783357.2

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-7.5252 -0.6071 -0.0046  0.6048  8.8075

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 8.012e-01  0.8951
                    s_lp        1.273e-01  0.3568  -1.00
 participant_number (Intercept) 9.135e+01  9.5575
                    s_lp        2.546e-01  0.5046  1.00
 document_id        (Intercept) 1.691e+00  1.3006
                    s_lp        9.177e-03  0.0958  1.00
 Residual                       3.141e+03 56.0486
Number of obs: 71918, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)   1.1328     1.8559 31.0224   0.610    0.546
s_lp          0.2244     0.2502 65.3476   0.897    0.373

Correlation of Fixed Effects:
     (Intr)
s_lp 0.395
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(lp_p1_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |
    document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 788100.3

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-9.3803 -0.6041 -0.0026  0.6016 10.9555 

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 2.607e+00  1.61470
                    s_lp        4.814e-01  0.69386 -1.00
 participant_number (Intercept) 1.973e+02 14.04636
                    s_lp        5.619e+00  2.37052 -0.28
 document_id        (Intercept) 1.279e+00  1.13113
                    s_lp        4.540e-03  0.06738 1.00
 Residual                       3.351e+03 57.88961      
Number of obs: 71918, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error     df t value Pr(>|t|)
(Intercept)   -1.869      2.657 29.301  -0.704   0.4871
s_lp           1.024      0.526 26.208   1.948   0.0623 .
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp -0.227
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')


```{r}
summary(lp_n1_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |
    document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 800647

Scaled residuals:
     Min       1Q   Median       3Q      Max 
-10.3236  -0.5970  -0.0008   0.5944  13.7321

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 1.506e+01  3.8805
                    s_lp        1.589e+00  1.2604  -0.75
 participant_number (Intercept) 2.445e+02 15.6374
                    s_lp        6.013e+00  2.4521  0.22
 document_id        (Intercept) 4.076e-01  0.6384
                    s_lp        7.787e-02  0.2791  1.00
 Residual                       3.980e+03 63.0912
Number of obs: 71918, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)  
(Intercept)  -6.4060     2.9345 28.3803  -2.183   0.0375 *
s_lp         -0.2481     0.5752 32.2000  -0.431   0.6690
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp 0.191
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')


```{r}
reading_cond <- "SPR"

lp_early_content_m <- lmer(
    (early ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |>
        filter(reading_type == reading_cond) |>
        filter(pos %in% content_words)
)

lp_p1_content_m <- lmer(
    (p1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |>
        filter(reading_type == reading_cond) |>
        filter(pos %in% content_words)
)

lp_n1_content_m <- lmer(
    (n1 ~ s_lp +
        (s_lp | participant_number) +
        (s_lp | word) +
        (s_lp | document_id)
    ),
    data = sterp_early_df |>
        filter(reading_type == reading_cond) |>
        filter(pos %in% content_words)
)
```

```{r}
summary(lp_early_content_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (early ~ s_lp + (s_lp | participant_number) + (s_lp | word) +
    (s_lp | document_id))
   Data: filter(filter(sterp_early_df, reading_type == reading_cond),
    pos %in% content_words)

REML criterion at convergence: 382403.9

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-6.4927 -0.6089 -0.0098  0.5986  8.8175

Random effects:
 Groups             Name        Variance  Std.Dev.  Corr
 word               (Intercept) 0.000e+00  0.000000
                    s_lp        6.078e-06  0.002465  NaN
 participant_number (Intercept) 8.767e+01  9.363420
                    s_lp        1.597e-01  0.399584 1.00
 document_id        (Intercept) 1.931e+00  1.389618      
                    s_lp        1.863e-04  0.013651 -1.00
 Residual                       3.123e+03 55.881934
Number of obs: 35124, groups:
word, 1640; participant_number, 29; document_id, 8

Fixed effects:
             Estimate Std. Error        df t value Pr(>|t|)
(Intercept)   1.06575    1.85407  31.59560   0.575    0.569
s_lp          0.07733    0.30669 266.79346   0.252    0.801

Correlation of Fixed Effects:
     (Intr)
s_lp 0.288
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(lp_p1_content_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |
    document_id))
   Data: filter(filter(sterp_early_df, reading_type == reading_cond),
    pos %in% content_words)

REML criterion at convergence: 384927.2

Scaled residuals:
    Min      1Q  Median      3Q     Max
-7.2682 -0.6067 -0.0005  0.5968 10.8828 

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept)    2.9467  1.7166
                    s_lp           0.6204  0.7877  -1.00
 participant_number (Intercept)  239.2250 15.4669
                    s_lp           0.7617  0.8728  -0.30
 document_id        (Intercept)    2.3275  1.5256       
                    s_lp           0.0804  0.2836  1.00
 Residual                       3347.7149 57.8594
Number of obs: 35124, groups:
word, 1640; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)
(Intercept)  -2.5885     2.9555 29.7347  -0.876    0.388
s_lp          0.6581     0.3801 18.2548   1.732    0.100

Correlation of Fixed Effects:
     (Intr)
s_lp -0.041
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(lp_n1_content_m)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (n1 ~ s_lp + (s_lp | participant_number) + (s_lp | word) + (s_lp |  
    document_id))
   Data: filter(filter(sterp_early_df, reading_type == reading_cond),
    pos %in% content_words)

REML criterion at convergence: 391058.2

Scaled residuals:
     Min       1Q   Median       3Q      Max 
-10.3474  -0.5977  -0.0039   0.5912  13.7465

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 1.391e+01  3.72941
                    s_lp        1.058e+00  1.02856 -1.00
 participant_number (Intercept) 2.306e+02 15.18589
                    s_lp        5.267e-02  0.22950 1.00
 document_id        (Intercept) 1.809e-01  0.42530
                    s_lp        9.338e-03  0.09663 1.00 
 Residual                       3.977e+03 63.06474
Number of obs: 35124, groups:
word, 1640; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error       df t value Pr(>|t|)
(Intercept)  -5.9888     2.8631  27.7164  -2.092   0.0458 *
s_lp          0.0830     0.3649 143.3062   0.227   0.8204
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
     (Intr)
s_lp 0.168
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

Freq and p1
```{r}
reading_cond <- "SPR"

freq_p1_m1 <- lmer(
    (p1 ~ s_lp + s_freq +
        (s_lp + s_freq | participant_number) +
        (s_lp | word) +
        (s_lp + s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)

freq_p1_m2 <- lmer(
    (p1 ~ s_lp * s_freq +
        (s_lp * s_freq | participant_number) +
        (s_lp | word) +
        (s_lp * s_freq | document_id)
    ),
    data = sterp_early_df |> filter(reading_type == reading_cond)
)
```

```{r}
summary(freq_p1_m1)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp + s_freq + (s_lp + s_freq | participant_number) +
    (s_lp | word) + (s_lp + s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 788055.2

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-9.3854 -0.6054 -0.0020  0.6015 10.9848

Random effects:
 Groups             Name        Variance  Std.Dev. Corr       
 word               (Intercept) 2.552e+00  1.59735
                    s_lp        5.170e-01  0.71905 -1.00
 participant_number (Intercept) 1.963e+02 14.01074
                    s_lp        1.696e+00  1.30223 -0.08
                    s_freq      3.379e+00  1.83812 -0.48  0.91
 document_id        (Intercept) 1.282e+00  1.13218
                    s_lp        2.771e-03  0.05264 -0.50
                    s_freq      7.473e-02  0.27337  0.75 -0.94
 Residual                       3.349e+03 57.86877
Number of obs: 71918, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)  
(Intercept)  -1.8587     2.6500 29.4924  -0.701   0.4886
s_lp          0.8536     0.3814 35.5892   2.238   0.0316 *
s_freq        0.2407     0.4572 12.4527   0.526   0.6078
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
       (Intr) s_lp  
s_lp   -0.054
s_freq -0.322  0.234
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')

```{r}
summary(freq_p1_m2)
```
Linear mixed model fit by REML. t-tests use Satterthwaite's method [
lmerModLmerTest]
Formula: (p1 ~ s_lp * s_freq + (s_lp * s_freq | participant_number) +  
    (s_lp | word) + (s_lp * s_freq | document_id))
   Data: filter(sterp_early_df, reading_type == reading_cond)

REML criterion at convergence: 788045.3

Scaled residuals:
    Min      1Q  Median      3Q     Max 
-9.3855 -0.6052 -0.0022  0.6015 10.9687

Random effects:
 Groups             Name        Variance  Std.Dev. Corr
 word               (Intercept) 2.653e+00  1.6289
                    s_lp        5.400e-01  0.7348  -1.00
 participant_number (Intercept) 1.982e+02 14.0781
                    s_lp        4.275e+00  2.0677  -0.09
                    s_freq      2.482e+00  1.5753  -0.56  0.87
                    s_lp:s_freq 7.751e-01  0.8804  -0.10  1.00  0.88
 document_id        (Intercept) 1.429e+00  1.1954
                    s_lp        9.643e-02  0.3105  -0.56
                    s_freq      2.712e-01  0.5208   0.59 -1.00      
                    s_lp:s_freq 1.191e-01  0.3450  -0.57  1.00 -1.00
 Residual                       3.348e+03 57.8624
Number of obs: 71918, groups:
word, 1975; participant_number, 29; document_id, 8

Fixed effects:
              Estimate Std. Error         df t value Pr(>|t|)
(Intercept) -1.8451195  2.6695807 29.3800124  -0.691    0.495
s_lp         0.8449960  0.5582474 26.6414115   1.514    0.142
s_freq       0.2387112  0.4581748 11.0471204   0.521    0.613
s_lp:s_freq -0.0001997  0.3517720 17.4994359  -0.001    1.000

Correlation of Fixed Effects:
            (Intr) s_lp   s_freq
s_lp        -0.106
s_freq      -0.302  0.096
s_lp:s_freq -0.121  0.763 -0.012
optimizer (nloptwrap) convergence code: 0 (OK)
boundary (singular) fit: see help('isSingular')